### 2014-06-24 paper/paper.tex
intro rough draft

\documentclass[a4paper, 12pt]{article}
\begin{document}
\pagenumbering{gobble}
\clearpage
\thispagestyle{empty}

\section{Introduction}

The problem.  The media is important to determine what people know about the world.  How the media gets its information is important as a result.  When media firms are getting information from their reporters they are getting infomration from other news media.

Our goal is to develop a model of media trust that accounts for trust in the media and how different media firms learn from each other.  Our model allows us to develop a network of trust between different media firms that allows for information diffusion between media firms.

We examine two novel datasets to investigate this model, the first is a dataset of tweets for a list of 3000 media firms in the United States from June to August of 2014.  Additionally, we consider a dataset of articles taken from the free archive ArXiv.  We build a trust network for both of these datasets based on a number of different measures of bias and use this to investigate our model.

We specify our model using a topic model comparable to the popular topic modeling approach, Latent Dirichlet Allocation.  We uses this to estimate the amount of information that different firms get from eachother and uses this as an estimate of trust.

We consider 6 predictions.  First, firms that share common beliefs are more likely to trust each other.  Second, firms that share commmon beliefs will communicate information faster.  Third, higher quality firms are more likely to be trusted by all firms.  Fourth, information that originates from multiple distance media sources is more likely to be accurate.  Fifth, neutral media sources are important in order to connect different biased groups.  Sixth and finally,

The paper is grouped as follows.  Section 2 presents the model and prior literature.  Section 3 convers the datasets used.  Section 4 covers the implementation of the model.  Section 5 presents the conclusions of the model.  Finally, summarizes and concludes.

\end{document}

### 2014-06-24 arxiv_scraper.py

@@ -1,7 +1,8 @@
 from BeautifulSoup import BeautifulSoup
 import cPickle
+from datetime import datetime
 import requests
-import slat
+import time
 
 
 def getCategories(url):
@@ -33,8 +34,8 @@ def getMonths(url, year):
     base_pg = requests.get(url + year)
     soup = BeautifulSoup(base_pg.text)
     months = [a.find("a")["href"] for a in soup.find("ul").findAll("li")]
-    num_1 = [a.find("b") for a in soup.find("ul").findAll("li")]
-    num_2 = [a.find("i") for a in soup.find("ul").findAll("li")]
+    num_1 = [a.find("b").text for a in soup.find("ul").findAll("li")]
+    num_2 = [a.find("i").text for a in soup.find("ul").findAll("li")]
     num = [x + y for x, y in zip(num_1, num_2)]
     return months, num
 
@@ -43,13 +44,13 @@ def getArticleUrls(url, month, max_ind, t_sleep):
     """gets all the articles for a month"""
 
     articles = []
-    for i in range(max_ind / 2000 + 1):
+    for i in range(0, int(max_ind) / 2000 + 1, 2000):
         if i > 0:
             # only sleep if there is more than one page, otherwise the sleep
             # is external
             time.sleep(t_sleep)
-        base_pg = requests.get(url + year, data={"show": (i + 1) * 2000,
-                                                 "skip": i * 2000})
+        base_pg = requests.get(url + month, data={"show": (i + 1) * 2000,
+                                                  "skip": i * 2000})
         soup = BeautifulSoup(base_pg.text)
         articles.extend([a["href"] for a in
                          soup.findAll("a", {"title": "Abstract"})])
@@ -83,27 +84,35 @@ def getArticle(url, a_url):
     return article_dict
 
 
-def fullRun(url, t_sleep, url_f, output_f):
+def fullRun(url, t_sleep, url_f, output_f, start_ind, urls=True):
     """gets all the articles"""
 
-    article_urls = []
-    articles = []
-    categories = getCategories(url)
-    time.sleep(t_sleep)
-    for c in categories:
-        years = getYears(url, c)
+    if urls:
+        t_1 = datetime.now()
+        article_urls = []
+        articles = []
+        categories = getCategories(url)
         time.sleep(t_sleep)
-        for y in years:
-            months, max_ind = getMonths(url, y)
+        for c in categories:
+            years = getYears(url, c)
[…]

### 2014-06-24 paper/paper.tex
add lit review

@@
-\documentclass[a4paper, 12pt]{article}
+%
+%
+\documentclass[a4paper]{article}
+
+\usepackage[english]{babel}
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage[colorinlistoftodos]{todonotes}
+
+\title{Social Learning in the Media: The Importance of Bias for Trust Between Media Firms}
+\author{Joseph Leland Bybee}
+\date{\today}
+
 \begin{document}
-\pagenumbering{gobble}
-\clearpage
-\thispagestyle{empty}
+
+\maketitle
 
@@
 How the media gets its information is important as a result.
-When media firms are getting information from their reporters they are getting infomration from other news media.
+When media firms are getting information from their reporters they are getting information from other news media.
 
@@
 
-We examine two novel datasets to investigate this model, the first is a dataset of tweets for a list of 3000 media firms in the United States from June to August of 2014.
-Additionally, we consider a dataset of articles taken from the free archive ArXiv.
-We build a trust network for both of these datasets based on a number of different measures of bias and use this to investigate our model.
+We examine two novel data sets to investigate this model, the first is a data set of tweets for a list of 3000 media firms in the United States from June to August of 2014.
+Additionally, we consider a data set of articles taken from the free archive ArXiv.
+We build a trust network for both of these data sets based on a number of different measures of bias and use this to investigate our model.
 
-We specify our model using a topic model comparable to the popular topic modeling approach, Latent Dirichlet Allocation.
-We uses this to estimate the amount of information that different firms get from eachother and uses this as an estimate of trust.
+We specify our model using a topic model comparable to the popular topic modeling approach, Latent Dirichlet Allocation (LDA).
+We uses this to estimate the amount of information that different firms get from each other and uses this as an estimate of trust.
 
@@
 First, firms that share common beliefs are more likely to trust each other.
-Second, firms that share commmon beliefs will communicate information faster.
+Second, firms that share common beliefs will communicate information faster.
 Third, higher quality firms are more likely to be trusted by all firms.
@@
 The paper is grouped as follows.
-Section 2 presents the model and prior literature.
-Section 3 convers the datasets used.
-Section 4 covers the implementation of the model.
-Section 5 presents the conclusions of the model.
-Finally, summarizes and concludes.
+Section 2 presents the prior literature.
+Section 3 develops the model used throughout.
+Section 4 covers the data sets used.
+Section 5 covers the implementation of the model.
+Section 6 presents the results.
+Finally, Section 7 summarizes and concludes.
+
+\section{Literature Review}
+
+We draw heavily from Gentzkow and Shapiro's 2006 paper \emph{Media Bias and Reputation}\footnote{Gentzkow and Shapiro.
+Media Bias and Reputation.
+2006}.
+Gentzkow and Shapiro develop a model where media firms bias their reporting to align with the beliefs of their market to maximize profits.
+We generalize this model to a network of media firms, where each firm learns from the actions of other firms in the network.
+
+To estimate media bias we consider a number of different measures drawn from several different sources.
+Groseclose and Milyo develop a measure that looks at the citations made by different media firms and how these coincide with the citations made by members of Congress\footnote{Groseclose and Milyo.
+A Measure of Media Bias.
+2005.}.
+Similarlly, Gentzkow and Shapiro develop a measure of media slant that uses the similarity between words used by different media outlets and members of Congress\footnote{Gentzkow and Shapiro.
+What Drives Media Slant?
+Evidence from U.S.
+Daily Newspaper.
+2006.}.
+Finally, Chiang and Knight develop a model of media bias that looks at endorsements made by media firms\footnote{Chiang and Knight.
+Media Bias and Influence: Evidence from Newspaper Endorsements.
+2011.}.
+
+The literature on slant in academia is more limited than in the media case, perhaps because the impact is less apparent.
+Much of the literature focuses on divisions on citation networks, though some looking at text clustering including one example presented below.
+Onder and Tervio look at the division of citation networks into "freshwater" and "saltwater" departments for economics.
+They find that the division is very real and significant in a number of cases\footnote{Onder and Tervio.
+Is Economics a House Divided?
+Analysis of Citation Networks.
+2014.}.
+
+The key work we draw from in the social learning literature is Acemoglu et.
+al's 2011 paper \emph{Bayesian Learning in Social Networks}\footnote{Acemoglu, Dahleh, Lobel and Ozdaglar.
+Bayesian Learning in Social Networks.
+2011.}.
+They develop a model of Bayesian social learning the is built around a stochastic network similar to teh one we develop here.
+They derive a number of general conclusions that are significant to this type of model.
+Acemoglu et.
+al's work on social learning in endogenous social networks is also significant as it mirrors the network structure we develop here\footnote{Acemoglu, Bimpikis and Ozdaglar.
+Dynamic of Information Exchange in Endogenous Social Networks.
+2013.}.
+Non Bayesian approaches have also been considered in the literature including Jadbabaie et.
+al's work\footnote{Jadbabaie, Molavi, Sandroni and Tahbaz-Salehi.
+Non-Bayesian Social Learning.
+2012.}.
+
+There is a large literature on more general information diffusion.
+Young provides a good overview of how the social learning methods popular in economics compare to those used in other fields\footnote{Young.
+Innovation Diffusion in Heterogeneous Populations: Contagion, Social Influence and Social Learning.
+2014.}.
+Golub and Jackson study how homophily affects diffusion and learning in networks.
+Their results are directly relevant to the work done here\footnote{Golub and Jackson.
+How Homophily Affects Learning and Diffusion in Networks.
+2009.}.
+ Yang and Leskovec develop a general model of information diffusion in implicit networks.
+This is significant here because in most cases the network structure for our model is implicit\footnote{Yang and Leskovec.
+Modeling Information Diffusion in Implicit Networks.
+2010.}.
+
+The method we use to estimate our model has its roots in the topic modeling literature, in particular the idea of LDA, first proposed by Blei, Ng and Jordan\footnote{Blei, Ng, Jordan.
+Latent Dirichlet Allocation.
+2003.}.
+LDA is essentially a hierarchical model where it is assumed that each word in a document is drawn from some topic distribution that is drawn for each document.
+Using this hierarchical model Blei, Ng and Jordan proposed a method to estimate the underlying topic distribution for a set of documents.
+Since their seminal paper the literature has exploded with examples of topic models.
+Blei provides a good survey of the methodology\footnote{Blei.
+Probabilitic Topic Models.
+2012}.
+
+Two key variants that are important here are dynamic topic models and author topic models.  A combination of these ideas form the basis for the estimation procedure used in this paper.  Blei
+and Lafferty introduce the idea of dynamic topic models to represent how topic may change over time\footnote{Blei and Lafferty.
+Dynamic Topic Models.
+2006}.
+They assume that the underlying topic proportions are drawn from some multivariate normal distribution centered around the prior topic distribution.
+While we don't use the same implementation here, the idea a dynamic topic is essential to our work as our estimates for the trust edges represent how much a news story influences the underlying topic distribution for other media firms.
+Rosen-Zvi et.
+al present another important variant in the idea of author topic models\footnote{Rosen-Zvi, Griffiths, Steyvers, Smyth.
+The Author-Topic Model for Authors and Documents.
+2004.}.
+Their model assumes that each author has some underlying preference for certain topics that can be used to cluster documents.
+While we don't directly implement this procedure the idea of a biased view of topics tied to each author is important to our model.
+
+A number of studies have used similar methods to investigate similar datasets to ours.
+Hong and Davison investigate and author topic model in the Twitter context to determine how Twitter users cluster and share information\footnote{Hong and Davison.
+Empirical Study of Topic Modeling in Twitter.
+2010.}.
+Grant et.
+al develop an online approach to estimating topics in the Twitter search context\footnote{Grant, George, Jenneisch and Wilson.
+Online Topic Modeling for Real-time Twitter Search.
+2011.}.
+Zhao et.
+al use a topic model to compare Twitter media to traditional media sources\footnote{Zhao, Jiang, Weng, He, Lim, Yan and Li.
+2011.}.
+Finally, Blei and Lafferty use a correlated topic model to estimate correlation within the scientific community using an academic article data set similar to the one used here\footnote{Blei and Lafferty.
+A Correlated Topic Model of Science.
+2007.}.
 

### 2014-06-24 arxiv_scraper.py

@@ -84,25 +84,30 @@ def getArticle(url, a_url):
     return article_dict
 
 
-def fullRun(url, t_sleep, url_f, output_f, start_ind, urls=True):
+def fullRun(url, t_sleep, url_f, output_f, backup_f, start_ind, urls=True):
     """gets all the articles"""
 
     if urls:
+        backup = open(backup_f, "wb")
         t_1 = datetime.now()
         article_urls = []
         articles = []
         categories = getCategories(url)
+        categories[14] = "/archive/cs"
         time.sleep(t_sleep)
-        for c in categories:
+        for i, c in enumerate(categories):
             years = getYears(url, c)
             time.sleep(t_sleep)
-            for y in years:
+            for j, y in enumerate(years):
                 months, max_ind = getMonths(url, y)
                 time.sleep(t_sleep)
                 for m, m_i in zip(months, max_ind):
-                    articles.extend(getArticleUrls(url, m, m_i, t_sleep))
+                    temp_urls = getArticleUrls(url, m, m_i, t_sleep)
+                    for u in temp_urls:
+                        backup.write(u + "\n")
+                    articles.extend(temp_urls)
                     time.sleep(t_sleep)
-                    print c.split("/")[-1], y.split("/")[-1], m.split("/")[-1], datetime.now() - t_1
+                    print c.split("/")[-1], y.split("/")[-1], m.split("/")[-1], datetime.now() - t_1, i, j
         cPickle.dump(article_urls, open(url_f, "wb"))
         print "got urls"
     else:

### 2014-07-01 paper/paper.tex
full model

@@
 \title{Social Learning in the Media: The Importance of Bias for Trust Between Media Firms}
-\author{Joseph Leland Bybee}
+\author{Bryan Kelly, Joseph Leland Bybee}
 \date{\today}
@@
 
+\section{Model}
+
+As with the Gentzkow and Shapiro model, we assume that there are two states of the world
+
+\[S \in [L,R].\]
+
+There are $N$ distinct populations that each make a decision
+
+\[A_i \in [L, R].\]
+
+The $i$th population will receive a positive payoff in the case that $A_i = S$ and a payoff of zero otherwise.  Each population has a prior belief about the state of the world
+
+\[P_i^c(R) = \theta_i^c.\]
+
+For each population there is a monopolist news firm that has a prior belief about the state of the world
+
+\[P_i(R) = \theta_i.\]
+
+Each news firm receives a signal about the state of the world
+
+\[s_i \in[l, r]\]
+
+and can report their signal (or a variation of their signal) to their population.
+There is some probability $\lambda$ that a given news firm is high quality.
+A high quality news firm is a news firm that receives a perfect signal of the world in each period, that is
+
+\[p_i(l|L) = p_i(r|R) =1.\]
+
+Alternatively, a firm can be a normal quality firm.  If this is the case than there is a probability $\pi_i$ that the firms receives a signal that aligns with the state of the world
+
+\[p_i(l|L) = p_i(r|R) = \pi_i.\]
+
+Each firm can publish a report based on their signal
+
+\[\hat{s}_i \in [\hat{l}, \hat{r}].\]
+
+Gentzkow and Shapiro show that the optimal strategy for a high quality firm is to always report the truth, that is
+
+\[\hat{s}_i = s_i.\]
+
+However, for the normal quality firm it may be better to lie.  Each firm can chose a strategy based on their signal
+
+\[\sigma_{is}(\hat{s}) = p_i(\hat{s}|s).\]
+
+For the remainder of this paper we constrain ourselves to the case where \[\sigma_{ir}(\hat{r}) > \sigma_{il}(\hat{l}).\]
+
+Gentzkow and Shapiro show that, in the case where a consumer receives no exogenous signal about the state of the world, their posterior beliefs about the quality of their monopolist news provider is a strictly increasing function of the likelihood ratio
+
+\[\frac{p(\hat{r}|\text{high}_i)}{p(\hat{r}|\text{normal}_i)}=\frac{\theta_i^c}{\theta_i^c[\sigma_r(\hat{r}_i) \pi_i + \sigma_l(\hat{r}_i)(1-\pi_i)] + (1 - \theta_c^i)[\sigma_r(\hat{r}_i)(1-\pi_i) + \sigma_l(\hat{l}_i)\pi_i]}\]
+
+This suggests that the higher $\theta_i^c$, the more likely that a consumer will believe the $i$th firm is of high quality.  In equilibrium they show that the expected gain for publishing $\hat{r}$ is
+
+\[\Delta(s)_i = (1 - \mu)\Delta^{nf}_i+\mu \Delta^f_i(s)\]
+
+where
+
+\[\Delta^{nf}_i =f(\lambda_i(\hat{r}, 0)) - f(\lambda_i(\hat{r}, 1)\]
+
+and
+
+\[\Delta^f_i(s) = \theta_i(s)[f(\lambda_i(\hat{r}, R)) - f(0)] - (1-\theta_i(s))[f(\lambda_i(\hat{l},L) - f(0)]\]
+
+In the above, $\lambda_i(\hat{s},0)$ represents the consumers posterior belief about the quality of the $i$th firm in the case of no feedback and $\lambda_i(\hat{s},S)$ represents the consumers posterior belief about the quality of the $i$th firm in the case of feedback.
+$\theta_i(s)$ is the $i$th firms posterior belief about the state of the world after receiving their signal $s_i$.
+Gentzkow and Shapiro show that under equilibrium conditions it is in a normal media firms interests to skew their reporting to align with the consumers priors about the state of the world.
+
+\subsection{Inter-Firm Trust}
+
+We now consider the situations in which firms can learn from each other.
+We assume that in equilibrium the $i$th firm generally publish articles that align with their consumers priors, $\theta_i^c$ and that the firms priors should reflect this, so $\theta_i \approx \theta_i^c$.
+$\theta_i$ can then be thought of as the proportion of news stories published by the $i$th firm that correspond to the $R$ state of the world.
+So then over $T$ periods we would expect $\theta_iT$ reports to be $\hat{r}$.
+Let's now turn to the $j$th firm's beliefs about the quality of the $i$th firm over $T$ periods.
+In each period, the $j$th firms beliefs should be
+
+ \[p_j(\text{high}_i|\hat{\textbf{s}}_{it}) = \frac{p_j(\hat{\textbf{s}}_{it}|\text{high}_i)p_j(\text{high}_i)}{p_j(\hat{\textbf{s}}_{it})}\]
+
+where $\hat{\textbf{s}}_{it}$ is a vector of the reports made by the $i$th firm.  Assuming that the beliefs follow the monotone likelihood ratio property we can show that
+
+\[p_j(\text{high}_i|\hat{\textbf{s}}_{it}) = \frac{p_j(\text{high}_i)}{1 + \frac{p_j(\hat{\textbf{s}}_{it}|\text{normal}_i)}{p_j(\hat{\textbf{s}}_{it}|\text{high}_i)}}\]
+
+This gives us the Gentzkow and Shapiro result that $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$ is a strictly increasing function of $\frac{p_j(\hat{\textbf{s}}_{it}|\text{high}_i)}{p_j(\hat{\textbf{s}}_{it}|\text{normal}_i)}$.
+Since the proportion of $\hat{\textbf{s}}_{it}$ that is $\hat{r}$ is an increasing function of $\theta_j$,  $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$ is an decreasing function of $\theta_j - \theta_i$, that is the more similar the $i$th firms beliefs are to those of the $j$th firm the more likely the $j$th firm is to believe the $i$th firm is high quality.
+
+We can use this idea to represent how much different news firms trust each other.
+We use this to help derive a number of bias free measures of truth and quality that could be used to help understand how the media market works.
+Throughout the remainder of this paper we will think of $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$ as the probability that the $j$th firm will incorporate the $i$th firms report into their own report.
+
+NOTE: I think the next two sections may be the most interesting but they still need a good deal of development.  I don't really know what to do with them.
+
+\subsection{Estimating Bias-Free Truth}
+
+Consider a case where you have $N$ firms, as before, however, each firm cannot observe the reports of the other firms.
+Additionally, assume that you are a Bayesian agent observing all $N$ firms and you want to get some estimate of the actual state of the world.
+You may have your prior belief about the state of the world
+
+\[p(R) = \theta\]
+
+Additionally, you have the reports for each of the $N$ firms as evidence.  Then what you might do is update your beliefs following Bayes rule
+
+ \[p(R|\hat{\textbf{s}}) \propto p(\hat{s}_1|R)...p(\hat{s}_N|R)p(R)\]
+
+ Unfortunately, this does not work in the case considered above because each firm can observe the reports of their fellow firms.
+Fortunately, since you have a measure of how much likely it is that each firm will incorporate the reports of another firm into their report, $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$.
+We could modify the above posterior to account for this, let $\gamma_ij$ represent $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$
+
+ \[p(R|\hat{\textbf{s}}) \propto (1-\gamma_{12})(1-\gamma_{13})...(1-\gamma_{1N})p(\hat{s}_1|R)...(1-\gamma_{N1})(1-\gamma_{N2})...(1-\gamma_{NN-1})p(\hat{s}_N|R)p(R)\]
+
+ We propose that this may be used as a measure to estimate the actual truth of a given state of the world.
+  One implication of this proposal is that we are more certain about the state of the world the more dispersed a set of signals are.  To see this consider a simple two agent case.
+
+\[p(R|\hat{\textbf{s}}) \propto (1-\gamma_{12})p(\hat{s}_1|R)(1-\gamma_{21})p(\hat{s}_2|R)p(R)\]
+
+In this case the more likely either firm trust the other ($\gamma_{12}$ is higher or$\gamma_{21}$ is higher), the lower $p(R|\hat{\textbf{s}})$.
+That is that if two firms share a similar belief about the state of the world and report the same signal that aligns with that state of the world, this says less than if two firms that have different beliefs report the same signal.
+
+\subsection{Estimating Bias-Free Quality}
+
+Next we propose a measure of bias-free quality for a given agent.
+One aspect of our model that has so far been ignored is the $j$th firm's prior beliefs about the quality of the $i$th firm.
+We could think of this prior as the equilibrium belief about the quality of the $i$th firm.
+Since $\theta_i$ and $\theta_j$ are the equilibrium beliefs for each firm about the state of the world, a reasonable choice for $p_j(H_i)$ might be $\theta_{ij}$, where $\theta_{ij} = \theta_i - \theta_j$.
+If we accept this prior we can then get an estimate for the likelihood function 
+\[p_j(\hat{\textbf{s}}_i|\text{high}_i) = \frac{p_j(\text{high}_i|\hat{\textbf{s}}_i)}{p_j(\text{high}_i)} = \frac{\gamma_ij}{\theta_ij}\]
+
+Using this measure we could then think like the Bayesian agent from the section above
+
+\[p(\text{high}_i|\hat{\textbf{s}}_i) \propto p(\hat{\textbf{s}}_i|\text{high}_i)p(\text{high}_i)\]
+
+\[= p_1(\hat{\textbf{s}}_i|\text{high}_i)p_2(\hat{\textbf{s}}_i|\text{high}_i)...p_N(\hat{\textbf{s}}_i|\text{high}_i)p(\text{high}_i)\]
+
+\[= \frac{\gamma_{1i}}{\theta_{1i}}\frac{\gamma_{2i}}{\theta_{2i}}...\frac{\gamma_{Ni}}{\theta_{Ni}}p(\text{high}_i)\]
+
+This would then suggest that our bias free estimate of quality would be an increasing function of the total trust in the $i$th firm, and a decreasing function of the shared beliefs with the $i$th firm.
+The intuition behind this measure is that higher quality firms should be more trusted by all firms controlling for bias.
+
+\subsection{The Significance of Border Cases}
+
+Next we consider the possibility for border agents.
+The intuition behind the idea for border agents is that they are agents who have a high enough $\gamma$ value for two different agents with rather low $\gamma$ values that they allow the communication of ideas between groups who otherwise would not communicate.
+More formally, consider a network with 3 agents, $i$, $j$, and $k$.
+If
+
+\[\gamma_{ij}\gamma_{jk} > \gamma_{ik}\]
+
+the $i$th agent is a border agent.  Border agents are important because they mean that given a lag two groups that otherwise would not receive the same information can receive the same information.
+
+We consider what proportion of the population of firms are border cases and how much information passes through the border cases.  This sub section may belong in a different section.
+
+\subsection{Risk Averse News Firms}
+
+Next we consider the possibility that there are risk averse media firms.
+These are firms that are more likely to trust firms that have a higher quality level controlling for bias.
+To estimate who the risk averse firms are we could assume the following relationship between trust, bias and bias-free quality
+
+\[\gamma_{ij} = \beta_1 \theta_{ij} + \beta_2 p(\text{high}_j|\hat{\textbf{s}}_j)\]
+
+Firms that are more risk averse should have a higher $\beta_2$ relative to the rest of the population of firms.  This may also fit better in a different section.
+
 \end{document}

### 2014-07-01 paper/paper.tex
review model

@@
 How the media gets its information is important as a result.
-When media firms are getting information from their reporters they are getting information from other news media.
+When media firms aren't getting information from their reporters they are getting information from other news firms.
 
@@
 We build a trust network for both of these data sets based on a number of different measures of bias and use this to investigate our model.
+NOTE: Obviously, if we are going to include this second dataset the problem will be generalized beyond media firms to some idea of "information agents".
 
@@
 
-We consider 6 predictions.
+We consider 5 predictions.
 First, firms that share common beliefs are more likely to trust each other.
@@
 Fifth, neutral media sources are important in order to connect different biased groups.
-Sixth and finally,
 
@@
 The literature on slant in academia is more limited than in the media case, perhaps because the impact is less apparent.
-Much of the literature focuses on divisions on citation networks, though some looking at text clustering including one example presented below.
+Much of the literature focuses on divisions of citation networks, though some look at text clustering including one example presented below.
 Onder and Tervio look at the division of citation networks into "freshwater" and "saltwater" departments for economics.
@@
 2011.}.
-They develop a model of Bayesian social learning the is built around a stochastic network similar to teh one we develop here.
+They develop a model of Bayesian social learning the is built around a stochastic network similar to the one we develop here.
 They derive a number of general conclusions that are significant to this type of model.
@@
  Yang and Leskovec develop a general model of information diffusion in implicit networks.
-This is significant here because in most cases the network structure for our model is implicit\footnote{Yang and Leskovec.
+This is significant here because the network structure for our model is implicit\footnote{Yang and Leskovec.
 Modeling Information Diffusion in Implicit Networks.
@@
 
-As with the Gentzkow and Shapiro model, we assume that there are two states of the world
+The roots of our model lie the Gentzkow and Shapiro paper \emph{Media Bias and Reputation}.  As with the Gentzkow and Shapiro model, we assume that there are two states of the world
 
@@
 
-For the remainder of this paper we constrain ourselves to the case where \[\sigma_{ir}(\hat{r}) > \sigma_{il}(\hat{l}).\]
+For the remainder of this paper we constrain ourselves to the case where
+
+\[\sigma_{ir}(\hat{r}) > \sigma_{il}(\hat{l}).\]
 
@@
 This gives us the Gentzkow and Shapiro result that $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$ is a strictly increasing function of $\frac{p_j(\hat{\textbf{s}}_{it}|\text{high}_i)}{p_j(\hat{\textbf{s}}_{it}|\text{normal}_i)}$.
-Since the proportion of $\hat{\textbf{s}}_{it}$ that is $\hat{r}$ is an increasing function of $\theta_j$,  $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$ is an decreasing function of $\theta_j - \theta_i$, that is the more similar the $i$th firms beliefs are to those of the $j$th firm the more likely the $j$th firm is to believe the $i$th firm is high quality.
+Since the proportion of $\hat{\textbf{s}}_{it}$ that is $\hat{r}$ is an increasing function of $\theta_j$,  $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$ is an decreasing function of $\theta_j - \theta_i$, that is, the more similar the $i$th firms beliefs are to those of the $j$th firm the more likely the $j$th firm is to believe the $i$th firm is high quality.
 
 We can use this idea to represent how much different news firms trust each other.
-We use this to help derive a number of bias free measures of truth and quality that could be used to help understand how the media market works.
+We use this to help derive a number of bias-free measures of truth and quality that could be used to help understand how the media market works.
 Throughout the remainder of this paper we will think of $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$ as the probability that the $j$th firm will incorporate the $i$th firms report into their own report.
@@
 
- Unfortunately, this does not work in the case considered above because each firm can observe the reports of their fellow firms.
-Fortunately, since you have a measure of how much likely it is that each firm will incorporate the reports of another firm into their report, $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$.
+ Unfortunately, this does not work in the case considered above because each firm can observe the reports of their fellow firms, so it is possible you may observe duplicate information.
+To account for this we need to account for how much firms trust each other and how likely they are to borrow information from other firms.
+Fortunately, you have a measure of how much likely it is that each firm will incorporate the reports of another firm into their report, $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$.
 We could modify the above posterior to account for this, let $\gamma_ij$ represent $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$
-
+ x
  \[p(R|\hat{\textbf{s}}) \propto (1-\gamma_{12})(1-\gamma_{13})...(1-\gamma_{1N})p(\hat{s}_1|R)...(1-\gamma_{N1})(1-\gamma_{N2})...(1-\gamma_{NN-1})p(\hat{s}_N|R)p(R)\]
@@
 In this case the more likely either firm trust the other ($\gamma_{12}$ is higher or$\gamma_{21}$ is higher), the lower $p(R|\hat{\textbf{s}})$.
-That is that if two firms share a similar belief about the state of the world and report the same signal that aligns with that state of the world, this says less than if two firms that have different beliefs report the same signal.
+That is that if two firms share a similar belief about the state of the world and report the same signal, this says less than if two firms that have different beliefs report the same signal.
 
@@
 
-Using this measure we could then think like the Bayesian agent from the section above
+Using this measure we could then think like the Bayesian agent from the sub section above
 
@@
 
-We consider what proportion of the population of firms are border cases and how much information passes through the border cases.  This sub section may belong in a different section.
+We consider what proportion of the population of firms are border agents and how much information passes through the border agents.  NOTE: This sub section may belong in a different section.
 
@@
 Next we consider the possibility that there are risk averse media firms.
-These are firms that are more likely to trust firms that have a higher quality level controlling for bias.
+These are firms that are willing to pay a premium to avoid poor quality information.
+This premium may involve waiting longer to verify a report or only trusting higher quality firms.
+We say that these firms are more likely to trust firms that have a higher quality level controlling for bias than less risk averse firms.
 To estimate who the risk averse firms are we could assume the following relationship between trust, bias and bias-free quality
@@
 
-Firms that are more risk averse should have a higher $\beta_2$ relative to the rest of the population of firms.  This may also fit better in a different section.
+Firms that are more risk averse should have a higher $\beta_2$ relative to the rest of the population of firms. NOTE: This may also fit better in a different section.
 

### 2014-07-03 paper/paper.tex
implementation seciton

@@
 
+\section{Implementation}
+
+In order to estimate the trust between agents we specify a variation on the Dynamic Topic Model proposed by Blei and Lafferty\footnote{Blei and Lafferty.
+Dynamic Topic Model.
+2006.}.
+Topic models are a set of hierarchical models that assume a latent "topic" underlying the choice of words in a collection of documents.
+The classical model is Latent Dirichlet Allocation (LDA), proposed by Blei et al.\footnote{Blei, Ng and Jordan.
+Latent Dirichlet Allocation.
+2003}.
+Assume that you have a collection of documents $D$ where $D = \{\textbf{w}_1, \textbf{w}_2, ...
+\textbf{w}_m\}$.
+Each $\textbf{w}_i$ is a document consisting of a set of words $w = \{w_1, w_2, ..., w_n\}$.
+LDA specifies the following generating process for the collection of documents:
+
+\[\theta_m \sim \text{Dir}(\alpha)\]
+
+\[z_n \sim Mult(\theta_m)\]
+
+\[w_n \sim p(w_n | z_n, \beta) = Mult(\beta_z)\]
+
+That is, $\theta$ is drawn from a Dirichlet distribution for each document.
+Then $z_n$ is drawn for each word in the document, and the word is from a Multinomial disttribution contional on the specific $z_n$ drawn and $\beta$.
+$\beta$ is a probability matrix where $\beta_{ij} = p(w^j = 1|z^i =1)$.
+What makes LDA particularly interesting among the class of clustering models is that topic parameter is sampled for each individual word, allowing for a mixture of topics within a document.
+Ultimately LDA allows for the estimation of $\theta$ and $\textbf{z}$ which estimate the distribution of topics within a collection of documents.
+
+Variants of LDA have seen a great deal of success for modeling the popularity of certain ideas within a collection of documents, in particular we focus on the Dynamic Topic Model.
+Blei and Lafferty developed the Dynamic Topic Model to account for the changing distribution of topics over time.
+It allowed for more accurate estimation when faced with a time series of documents.
+The Dynamic Topic Model has a similar structure to LDA, however, it assumes time dependence for the $\alpha$ and $\beta$ parameters.
+
+\[\alpha_t | \alpha_{t-1} \sim N(\alpha_{t-1}, \delta^2I)\]
+
+\[\beta_t | \beta_{t-1} \sim N(\beta_{t-1}, \sigma^2I)\]
+
+\[\theta \sim N(\alpha_t, a^2I)\]
+
+\[z_{tn} \sim Mult(\pi(\theta))\]
+
+\[w_{tn} \sim Mult(\pi(\beta_{t, z}))\]
+
+This generation procedure allows the distribution of topics to change over time, accounting for shifts in the content of documents.
+Such a model is important for the dataset we wish to use where topics are changing regularly.
+We use a variant of the Dynamic Topic Model that allows for the distribution of $\alpha_{it}$ to be impacted by $\alpha_{-it-1}$.
+That is we assume that the underlying topic distribution is ultimately effected by the topic distributions for other agents in a network of agents.
+More formally we say that,
+
+\[\alpha_{it} \sim N(\textbf{\alpha}_{t-1}^T \gamma, \delta^2I)\]
+
+$\textbf{\alpha}$ is a vector of the $\alpha$ parameter for each of the $N$ agents, and $\gamma$ is an $N$ dimensional vector of weights for the $N$ agents.
+That is, $\alpha_{it}$ is drawn from a weighted sum of the $\alpha$ values for each agent in the prior period.
+$\gamma$ gives an estimate of the impact that each agent has on the topic distribution of the $i$th agent.
+We use $\gamma$ to represent our trust value discussed above.
+Unfortunately, this generating process does not have a conjugate form so we cannot using Gibbs sampling as used commonly with LDA.
+Instead we must use a more complicated Metropolis Hastings algorithm to estimate $\gamma$.
+
 \end{document}

### 2014-07-05 paper/paper.tex
full posterior

@@
  x
- \[p(R|\hat{\textbf{s}}) \propto (1-\gamma_{12})(1-\gamma_{13})...(1-\gamma_{1N})p(\hat{s}_1|R)...(1-\gamma_{N1})(1-\gamma_{N2})...(1-\gamma_{NN-1})p(\hat{s}_N|R)p(R)\]
+ \[p(R|\hat{\textbf{s}}) \propto (1-\gamma_{12})(1-\gamma_{13})...(1-\gamma_{1N})p(\hat{s}_1|R)...\]
+
+ \[(1-\gamma_{N1})(1-\gamma_{N2})...(1-\gamma_{NN-1})p(\hat{s}_N|R)p(R)\]
 
@@
 
-\[\alpha_{it} \sim N(\textbf{\alpha}_{t-1}^T \gamma, \delta^2I)\]
+\[\alpha_{it} \sim N(\alpha_{t-1}^T \gamma, \delta^2I)\]
 
-$\textbf{\alpha}$ is a vector of the $\alpha$ parameter for each of the $N$ agents, and $\gamma$ is an $N$ dimensional vector of weights for the $N$ agents.
+$\alpha$ is a vector of the $\alpha$ parameter for each of the $N$ agents, and $\gamma$ is an $N$ dimensional vector of weights for the $N$ agents.
 That is, $\alpha_{it}$ is drawn from a weighted sum of the $\alpha$ values for each agent in the prior period.
@@
 
+\newpage
+\appendix
+
+\section{Full Conditionals}
+
+\[p(\gamma_i | \mu, \xi^2) = N(\mu, \xi^2I)\]
+
+\[p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}. \gamma_i, \delta^2) = N(\text{\boldmath$\alpha$}^T_{t-1} \gamma_i, \delta^2I)\]
+
+\[p(\beta_t | \beta_{t-1}, \sigma^2) = N(\beta_{t-1}, \sigma^2I)\]
+
+\[p(\theta_{itd} | \alpha_{it}, a^2) = N(\alpha_{it}, a^2)\]
+
+\[p(z_{itnd}| \theta_{itd}) = Mult(\pi(\theta_{itd}))\]
+
+\[p(w_{itnd} | \beta_t, z_{itnd}) = Mult(\pi(\beta_t^{z_{itnd}}))\]
+
+\[p(\theta, \text{\boldmath$\gamma$}, \text{\boldmath$\alpha$}, \text{\boldmath$\beta$}, \textbf{z} | \textbf{w}) \propto \prod_{i=1}^M \prod_{t=1}^T \prod_{n=1}^N \prod_{d=1}^D p(w_{itnd}|z_{itnd}, \beta_t) p(\beta_t | \beta_{t-1}, \sigma^2) p(z_{itnd}|\theta_{itd})\]
+
+\[p(\theta_{itd}|\alpha_{it},a^2)p(\alpha_{it}|\text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \mu, \xi^2)\]
+
+\subsection{Posterior Specification for $z_i$}
+
 \end{document}

### 2014-07-06 arxiv_scraper.py
seperate function for getting articles

@@ -1,5 +1,6 @@
 from BeautifulSoup import BeautifulSoup
 import cPickle
+import unicodecsv
 from datetime import datetime
 import requests
 import time
@@ -83,6 +84,27 @@ def getArticle(url, a_url):
     doc = slate.PDF(input_)
     article_dict["text"] = doc
     return article_dict
+
+
+def writeArticleDictCSV(article, csv_f):
+    """writes the specified article to a csv"""
+
+    f = open(csv_f, "ab")
+    writer = unicodecsv.writer(f)
+    writer.writerow(article.values())
+    f.close()
+
+
+def getArticles(article_url_f, url, t_sleep, output_csv, start_ind):
+    """gets the articles from a list of urls"""
+
+    article_urls = cPickle.load(open(article_url_f, "rb"))
+    ln = len(article_urls)
+    t_1 = datetime.now()
+    for i, a in enumerate(article_urls[start_ind:]):
+        article = getArticle(url, a)
+        writeArticleDictCSV(article, output_csv)
+        print start_ind + i, (start_ind + i) * 100. / ln, datetime.now() - t_1
 
 
 def fullRun(url, t_sleep, url_f, output_f, backup_f, start_ind, urls=True):

### 2014-07-07 paper/paper.tex
write up appendix
review intro

@@
 
-\title{Social Learning in the Media: The Importance of Bias for Trust Between Media Firms}
+\title{DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion}
 \author{Bryan Kelly, Joseph Leland Bybee}
@@
 
+\begin{abstract}
+
+We investigate the impact that bias and trust has on how information is diffused within a network of agents.
+We use this model to investigate the information diffusion characteristics of 2 different data sets.
+We also use our measures of trust to estimate some probability for the real state of the world.
+Additionally, we estimate whether certain agents are higher quality than others based on how well they are trusted.
+Finally, we consider a measure of risk aversion related to how willing agents are to trust each other.
+
+\end{abstract}
+
 \section{Introduction}
 
-The problem.
-The media is important to determine what people know about the world.
-How the media gets its information is important as a result.
-When media firms aren't getting information from their reporters they are getting information from other news firms.
+Individuals often rely on the information and decisions of other individuals and companies to inform their understanding about how the world works.
+Consider the case two competing newspapers, firm A and B.
+If firm A sees a report about corruption at City Hall from firm B, this may influence what firm A publishes the next day and where they dedicate their investigative resources.
+This influence may be related to how much firm A trusts the reporting of firm B and how similar their beliefs about the world are.
 
-Our goal is to develop a model of media trust that accounts for trust in the media and how different media firms learn from each other.
-Our model allows us to develop a network of trust between different media firms that allows for information diffusion between media firms.
+We consider a general model of social learning, motivated by the above hypothetical, where agents learn from other agents in their network based on how much they trust the other agents.
+We investigate the importance of this trust network to information diffusion and use it to help develop estimates of the actual state of the world and quality of different agents in the network.
 
-We examine two novel data sets to investigate this model, the first is a data set of tweets for a list of 3000 media firms in the United States from June to August of 2014.
-Additionally, we consider a data set of articles taken from the free archive ArXiv.
+We examine two novel data sets to investigate this model, the first is a data set of tweets for a list of roughly 3000 media firms in the United States from June to August of 2014.
+Additionally, we consider a data set of articles taken from the preprint repository ArXiv.
 We build a trust network for both of these data sets based on a number of different measures of bias and use this to investigate our model.
-NOTE: Obviously, if we are going to include this second dataset the problem will be generalized beyond media firms to some idea of "information agents".
-
-We specify our model using a topic model comparable to the popular topic modeling approach, Latent Dirichlet Allocation (LDA).
-We uses this to estimate the amount of information that different firms get from each other and uses this as an estimate of trust.
+To investigate this model we use a graphical variant of the dynamic topic model to estimate trust between agents.
 
@@
 Fourth, information that originates from multiple distance media sources is more likely to be accurate.
-Fifth, neutral media sources are important in order to connect different biased groups.
+Fifth, neutral media sources are important to the complete diffusion of information.
 
@@
 
-\[p(\theta_{itd} | \alpha_{it}, a^2) = N(\alpha_{it}, a^2)\]
+\[p(\theta | \alpha_{it}, a^2) = N(\alpha_{it}, a^2I)\]
 
-\[p(z_{itnd}| \theta_{itd}) = Mult(\pi(\theta_{itd}))\]
+\[p(\phi | \beta_t, b^2) = N(\beta_t, b^2I)\]
 
-\[p(w_{itnd} | \beta_t, z_{itnd}) = Mult(\pi(\beta_t^{z_{itnd}}))\]
+\[p(z| \theta) = Mult(\pi(\theta))\]
 
-\[p(\theta, \text{\boldmath$\gamma$}, \text{\boldmath$\alpha$}, \text{\boldmath$\beta$}, \textbf{z} | \textbf{w}) \propto \prod_{i=1}^M \prod_{t=1}^T \prod_{n=1}^N \prod_{d=1}^D p(w_{itnd}|z_{itnd}, \beta_t) p(\beta_t | \beta_{t-1}, \sigma^2) p(z_{itnd}|\theta_{itd})\]
+\[p(w | \phi, z) = Mult(\pi(\phi_z))\]
 
-\[p(\theta_{itd}|\alpha_{it},a^2)p(\alpha_{it}|\text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \mu, \xi^2)\]
+\[p(\theta, \phi, \gamma_i, \alpha_{it}, \beta_t, z | w) \propto p(w | \phi, z) p(\phi |  \beta_t, b^2)  p(z | \theta)  p(\beta_t | \beta_{t-1}, \sigma^2) p(\theta | \alpha_{it}, a^2) p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \mu, xi^2)\]
 
@@
 
+\[p(z_i | w_i, \theta, \phi) \propto p(z_i = k | \theta) p(w_i | z_i = k, \phi)\]
+
+\[= \frac{\theta_k}{\sum_k \theta} \frac{\phi_{k, w_i}}{\sum_v \phi_k}\]
+
+\subsection{Posterior Specification for $\beta_t$}
+
+\[p(\beta_t | \phi, \beta_{t-1}, b^2, \sigma^2) \propto p(\phi | \beta_t) p(\beta_t | \beta_{t-1})\]
+
+\[= N(\beta_t, b^2I) N(\beta_{t-1}, \sigma^2I)\]
+
+Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+
+\subsection{Posterior Specification for $\alpha_t$}
+
+\[p(\alpha_{it} | \theta, \text{\boldmath$\alpha$}_{t-1}, \gamma_i, a^2, \delta^2) \propto p(\theta | \alpha_{it}) p(\alpha_t | \text{\boldmath$\alpha$}, \gamma_i)\]
+
+\[= N(\alpha_{it}, a^2I) N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)\]
+
+Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+
+\subsection{Posterior Specification for $\gamma$}
+
+\[p(\gamma_i | \alpha_{it}, \text{\boldmath$\alpha$}_{t-1}, \mu, \xi^2) \propto p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \mu, \xi^2)\]
+
+\[= N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)N(\mu, \xi^2)\]
+
+Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+
+\subsection{Posterior Specification for $\theta$}
+
+\[p(\theta | z, \alpha_{it}, \delta^2) \propto p(z | \theta) p(\theta | \alpha_{it}, \delta^2)\]
+
+\[= Mult(\pi(\theta)) N(\alpha_{it}, \delta^2I)\]
+
+Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+
+\subsection{Posterior Specification for $\phi$}
+
+\[p(\phi_k | \beta_t, z, w, b^2) \propto p(w | \phi_k, z) p(\phi_k | \beta_t)\]
+
+\[= Mult(\pi(phi_{k,z})) N(\beta_t, b^2)\]
+
+Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+
 \end{document}

### 2014-07-07 paper/paper.tex
fix paper

@@
 Gentzkow and Shapiro develop a model where media firms bias their reporting to align with the beliefs of their market to maximize profits.
-We generalize this model to a network of media firms, where each firm learns from the actions of other firms in the network.
+We generalize this model to a network of agents, where each agent learns from the actions of other agents in the network, as well as their own exogenous signals.
 
-To estimate media bias we consider a number of different measures drawn from several different sources.
+To estimate media bias we consider a number of different measures.
 Groseclose and Milyo develop a measure that looks at the citations made by different media firms and how these coincide with the citations made by members of Congress\footnote{Groseclose and Milyo.
@@
 2011.}.
-They develop a model of Bayesian social learning the is built around a stochastic network similar to the one we develop here.
+They develop a model of Bayesian social learning that is built around a stochastic network similar to the one we develop here.
 They derive a number of general conclusions that are significant to this type of model.
@@
 Non-Bayesian Social Learning.
-2012.}.
+2012.}, though we don't follow that approach here.
 
 There is a large literature on more general information diffusion.
-Young provides a good overview of how the social learning methods popular in economics compare to those used in other fields\footnote{Young.
+Young provides a good overview of how the social learning methods, popular in economics, compare to those used in other fields\footnote{Young.
 Innovation Diffusion in Heterogeneous Populations: Contagion, Social Influence and Social Learning.
@@
 
-The method we use to estimate our model has its roots in the topic modeling literature, in particular the idea of LDA, first proposed by Blei, Ng and Jordan\footnote{Blei, Ng, Jordan.
+The method we use to estimate our model has its roots in the topic modeling literature, in particular the idea of Latent Dirichlet Allocation (LDA), first proposed by Blei, Ng and Jordan\footnote{Blei, Ng, Jordan.
 Latent Dirichlet Allocation.
@@
 They assume that the underlying topic proportions are drawn from some multivariate normal distribution centered around the prior topic distribution.
-While we don't use the same implementation here, the idea a dynamic topic is essential to our work as our estimates for the trust edges represent how much a news story influences the underlying topic distribution for other media firms.
+Our approach is an application of this method.
 Rosen-Zvi et.
@@
 A number of studies have used similar methods to investigate similar datasets to ours.
-Hong and Davison investigate and author topic model in the Twitter context to determine how Twitter users cluster and share information\footnote{Hong and Davison.
+Hong and Davison investigate an author topic model in the Twitter context to determine how Twitter users cluster and share information\footnote{Hong and Davison.
 Empirical Study of Topic Modeling in Twitter.
@@
 
-The roots of our model lie the Gentzkow and Shapiro paper \emph{Media Bias and Reputation}.  As with the Gentzkow and Shapiro model, we assume that there are two states of the world
+The roots of our model lie the Gentzkow and Shapiro paper \emph{Media Bias and Reputation}.
+For now we focus on the case used in their paper with a media firm and consumer.
+The approach works just as well in the case of a general network of agents.
+As with the Gentzkow and Shapiro model, we assume that there are two states of the world
 
@@
 
-Gentzkow and Shapiro show that, in the case where a consumer receives no exogenous signal about the state of the world, their posterior beliefs about the quality of their monopolist news provider is a strictly increasing function of the likelihood ratio
+Gentzkow and Shapiro show that, in the case where a consumer receives no exogenous signal about the state of the world, their posterior beliefs about the quality of their news provider is a strictly increasing function of the likelihood ratio
 
@@
 
-This suggests that the higher $\theta_i^c$, the more likely that a consumer will believe the $i$th firm is of high quality.  In equilibrium they show that the expected gain for publishing $\hat{r}$ is
+This suggests that the higher $\theta_i^c$, the more likely  a consumer will believe the $i$th firm is of high quality.  In equilibrium they show that the expected gain for publishing $\hat{r}$ is
 
@@
 $\theta_i(s)$ is the $i$th firms posterior belief about the state of the world after receiving their signal $s_i$.
-Gentzkow and Shapiro show that under equilibrium conditions it is in a normal media firms interests to skew their reporting to align with the consumers priors about the state of the world.
-
+Gentzkow and Shapiro show that under equilibrium conditions it is in a normal media firms interests to skew their reporting to align with the consumers priors about the state of the world, because their consumers are more likely to trust them in this case.
 \subsection{Inter-Firm Trust}
@@
 We now consider the situations in which firms can learn from each other.
-We assume that in equilibrium the $i$th firm generally publish articles that align with their consumers priors, $\theta_i^c$ and that the firms priors should reflect this, so $\theta_i \approx \theta_i^c$.
+We assume that in equilibrium the $i$th firm publishes articles that align with their consumers priors, $\theta_i^c$ and that the firms priors should reflect this, so $\theta_i \approx \theta_i^c$.
 $\theta_i$ can then be thought of as the proportion of news stories published by the $i$th firm that correspond to the $R$ state of the world.
 So then over $T$ periods we would expect $\theta_iT$ reports to be $\hat{r}$.
-Let's now turn to the $j$th firm's beliefs about the quality of the $i$th firm over $T$ periods.
-In each period, the $j$th firms beliefs should be
+
+Let's now turn to the $j$th firm's beliefs about the quality of the $i$th firm over $T$ periods.  In each period, the $j$th firms beliefs should be
 
@@
 
-where $\hat{\textbf{s}}_{it}$ is a vector of the reports made by the $i$th firm.  Assuming that the beliefs follow the monotone likelihood ratio property we can show that
+where $\hat{\textbf{s}}_{it}$ is a vector of the reports made by the $i$th firm as of period $t$.  Assuming that the beliefs follow the monotone likelihood ratio property we can show that
 
@@
 
- Unfortunately, this does not work in the case considered above because each firm can observe the reports of their fellow firms, so it is possible you may observe duplicate information.
+ Unfortunately, this does not work in the case where firms can observe the reports of other firms, because it is possible you may observe duplicate information.
 To account for this we need to account for how much firms trust each other and how likely they are to borrow information from other firms.
@@
 We could modify the above posterior to account for this, let $\gamma_ij$ represent $p_j(\text{high}_i|\hat{\textbf{s}}_{it})$
- x
+
  \[p(R|\hat{\textbf{s}}) \propto (1-\gamma_{12})(1-\gamma_{13})...(1-\gamma_{1N})p(\hat{s}_1|R)...\]
@@
 
-In this case the more likely either firm trust the other ($\gamma_{12}$ is higher or$\gamma_{21}$ is higher), the lower $p(R|\hat{\textbf{s}})$.
+In this case the more likely either firm trust the other ($\gamma_{12}$ is higher or $\gamma_{21}$ is higher), the lower $p(R|\hat{\textbf{s}})$.
 That is that if two firms share a similar belief about the state of the world and report the same signal, this says less than if two firms that have different beliefs report the same signal.
@@
 
-Next we consider the possibility for border agents.
+Next we consider the possibility of border agents.
 The intuition behind the idea for border agents is that they are agents who have a high enough $\gamma$ value for two different agents with rather low $\gamma$ values that they allow the communication of ideas between groups who otherwise would not communicate.
@@
 
-the $i$th agent is a border agent.  Border agents are important because they mean that given a lag two groups that otherwise would not receive the same information can receive the same information.
+the $j$th agent is a border agent.  Border agents are important because they mean that given a lag two groups that otherwise would not receive the same information can receive the same information.
 
@@
 Next we consider the possibility that there are risk averse media firms.
-These are firms that are willing to pay a premium to avoid poor quality information.
+These are firms that are willing to pay a premium to avoid poor quality information, relative to other firms.
 This premium may involve waiting longer to verify a report or only trusting higher quality firms.
@@
 
-\[\theta_m \sim \text{Dir}(\alpha)\]
+\[\theta \sim \text{Dir}(\alpha)\]
 
-\[z_n \sim Mult(\theta_m)\]
+\[z_n \sim Mult(\theta)\]
 
-\[w_n \sim p(w_n | z_n, \beta) = Mult(\beta_z)\]
+\[\phi \sim Dir(\beta)\]
 
-That is, $\theta$ is drawn from a Dirichlet distribution for each document.
-Then $z_n$ is drawn for each word in the document, and the word is from a Multinomial disttribution contional on the specific $z_n$ drawn and $\beta$.
+\[w_n \sim  Mult(\phi_z)\]
+
+That is, $\theta$ is drawn from a Dirichlet distribution for each document,  $\phi$ is drawn from a Dirichlet distribution for each topic.
+Then $z_n$ is drawn for each word in the document, and the word is from a Multinomial disttribution for the $\phi$ for the specified topic $z_n$.
 $\beta$ is a probability matrix where $\beta_{ij} = p(w^j = 1|z^i =1)$.
 What makes LDA particularly interesting among the class of clustering models is that topic parameter is sampled for each individual word, allowing for a mixture of topics within a document.
-Ultimately LDA allows for the estimation of $\theta$ and $\textbf{z}$ which estimate the distribution of topics within a collection of documents.
+Ultimately LDA allows for the estimation of $\theta$, $\phi$ and $\textbf{z}$ which estimate the distribution of topics within a collection of documents.
 
@@
 
+\[\phi \sim N(\beta_t, b^2I)\]
+
 \[z_{tn} \sim Mult(\pi(\theta))\]
 
-\[w_{tn} \sim Mult(\pi(\beta_{t, z}))\]
+\[w_{tn} \sim Mult(\pi(\phi_z)\]
 
@@
 Such a model is important for the dataset we wish to use where topics are changing regularly.
-We use a variant of the Dynamic Topic Model that allows for the distribution of $\alpha_{it}$ to be impacted by $\alpha_{-it-1}$.
+We use a variant of the Dynamic Topic Model that allows for the distribution of $\alpha_{it}$ to be impacted by $\text{\boldmath$\alpha$}_{t-1}$.
+Where $\text{\boldmath$\alpha$}_{t-1}$ is a vector of the $\alpha_{it-1}$ values.
 That is we assume that the underlying topic distribution is ultimately effected by the topic distributions for other agents in a network of agents.
@@
 
-\[\alpha_{it} \sim N(\alpha_{t-1}^T \gamma, \delta^2I)\]
+\[\alpha_{it} \sim N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)\]
 
-$\alpha$ is a vector of the $\alpha$ parameter for each of the $N$ agents, and $\gamma$ is an $N$ dimensional vector of weights for the $N$ agents.
+$\gamma_i$ is an $N$ dimensional vector of weights for the $N$ agents for the $i$th agent.
 That is, $\alpha_{it}$ is drawn from a weighted sum of the $\alpha$ values for each agent in the prior period.
-$\gamma$ gives an estimate of the impact that each agent has on the topic distribution of the $i$th agent.
-We use $\gamma$ to represent our trust value discussed above.
+$\gamma_i$ gives an estimate of the impact that each agent has on the topic distribution of the $i$th agent.
+We use $\gamma_i$ to represent our trust value discussed above.
 Unfortunately, this generating process does not have a conjugate form so we cannot using Gibbs sampling as used commonly with LDA.
-Instead we must use a more complicated Metropolis Hastings algorithm to estimate $\gamma$.
+Instead we must use a more complicated Metropolis Hastings algorithm to estimate $\gamma_i$.
 
@@
 
+\[\propto \exp{\left(-\frac{1}{2}[(\phi - \beta_t)^T(\phi - \beta_t) + (\beta_t - \beta_{t-1})^T(\beta_t - \beta_{t-1})]\right)}\]
+
 Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
@@
 \[= N(\alpha_{it}, a^2I) N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)\]
+
+\[\propto \exp{\left(-\frac{1}{2}[(\theta - \alpha_{it})^T(\theta - \alpha_{it}) + (\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)]\right)}\]
 
@@
 
+\[\propto \exp{\left(-\frac{1}{2}[(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i) + (\gamma_i - \mu)^T(\gamma_i - \mu)]\right)}\]
+
 Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
@@
 \[= Mult(\pi(\theta)) N(\alpha_{it}, \delta^2I)\]
+
+\[\propto \left(\prod_{i=1}^N \prod_{k=1}^K \frac{\theta_k^{I_{z_i}=k}}{\sum_k \theta}\right) \left(\exp{-\frac{1}{2}(\theta - \alpha_{it})^T(\theta - \alpha_{it})}\right) \]
 
@@
 
+\[\propto \left(\prod_{i:z_i=k}^N \prod_{v=1}^V \frac{\phi_{k, v}^{I_{w_i}=v}}{\sum_v \phi_k}\right) \left(\exp{-\frac{1}{2}(\phi_k - \beta_t)^T(\phi_k - \beta_t)}\right) \]
+
 Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.

### 2014-07-08 paper/paper.tex
remove authors
correct posteriors

@@
 \title{DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion}
-\author{Bryan Kelly, Joseph Leland Bybee}
 \date{\today}
@@
 
-\subsection{Posterior Specification for $z_i$}
+\subsection{Posterior Specification for $z_{jit}$}
 
-\[p(z_i | w_i, \theta, \phi) \propto p(z_i = k | \theta) p(w_i | z_i = k, \phi)\]
+\[p(z_{jit} | w_{jit}, \theta_{it}, \phi_t) \propto p(z_{jit} = k | \theta_{it}) p(w_{jit} | z_{jit} = k, \phi_t)\]
 
-\[= \frac{\theta_k}{\sum_k \theta} \frac{\phi_{k, w_i}}{\sum_v \phi_k}\]
+\[= \frac{\theta_{it}^{I_{z_{jit}}=k}}{\sum_k \theta_{it}} \frac{\phi_{kt}^{I_{w_j}=v}}{\sum_v \phi_{kt}}\]
 
@@
 
-\[= N(\beta_t, b^2I) N(\beta_{t-1}, \sigma^2I)\]
+\[=  \prod_{k=1}^K N(\beta_t, b^2I) N(\beta_{t-1}, \sigma^2I)\]
 
-\[\propto \exp{\left(-\frac{1}{2}[(\phi - \beta_t)^T(\phi - \beta_t) + (\beta_t - \beta_{t-1})^T(\beta_t - \beta_{t-1})]\right)}\]
+\[\propto \exp{\left(\sum_{k=1}^K(\phi_k - \beta_{t})^T(\phi_k - \beta_{t}) + (\beta_{t} - \beta_{t-1})^T(\beta_{t} - \beta_{t-1})\right)}\]
 
@@
 
-\subsection{Posterior Specification for $\alpha_t$}
+\subsection{Posterior Specification for $\alpha_{it}$}
 
@@
 
-\[= N(\alpha_{it}, a^2I) N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)\]
+\[= \prod_{d=1}^{D_i} N(\alpha_{it}, a^2I) N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)\]
 
-\[\propto \exp{\left(-\frac{1}{2}[(\theta - \alpha_{it})^T(\theta - \alpha_{it}) + (\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)]\right)}\]
+\[\propto \exp{\left(\sum_{d=1}^{D_i}(\theta_d - \alpha_{it})^T(\theta_d - \alpha_{it}) + (\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)\right)}\]
 
@@
 
-\subsection{Posterior Specification for $\gamma$}
+\subsection{Posterior Specification for $\gamma_i$}
 
@@
 
-\[= N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)N(\mu, \xi^2)\]
+\[= \prod_{t=2}^T N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)N(\mu, \xi^2)\]
 
-\[\propto \exp{\left(-\frac{1}{2}[(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i) + (\gamma_i - \mu)^T(\gamma_i - \mu)]\right)}\]
+\[\propto \exp{\left(\sum_{t=2}^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i) + (\gamma_i - \mu)^T(\gamma_i - \mu)\right)}\]
 
@@
 
-\subsection{Posterior Specification for $\theta$}
+\subsection{Posterior Specification for $\theta_{it}$}
 
-\[p(\theta | z, \alpha_{it}, \delta^2) \propto p(z | \theta) p(\theta | \alpha_{it}, \delta^2)\]
+\[p(\theta_{it} | z, \alpha_{it}, \delta^2) \propto p(z | \theta_{it}) p(\theta_{it} | \alpha_{it}, \delta^2)\]
 
-\[= Mult(\pi(\theta)) N(\alpha_{it}, \delta^2I)\]
+\[= \prod_{d=1}^D \prod_{j=1}^{J_d} Mult(\pi(\theta_{dit}))\prod_{d=1}^D N(\alpha_{it}, \delta^2I)\]
 
-\[\propto \left(\prod_{i=1}^N \prod_{k=1}^K \frac{\theta_k^{I_{z_i}=k}}{\sum_k \theta}\right) \left(\exp{-\frac{1}{2}(\theta - \alpha_{it})^T(\theta - \alpha_{it})}\right) \]
+\[\propto \left(\prod_{d=1}^D \prod_{j=1}^{J_d} \frac{\theta_{dit}^{I_{z_j}=k}}{\sum_k \theta_{dit}}\right) \exp{\left(\sum_{d=1}^D(\theta_{dit} - \alpha_{it})^T(\theta_{dit} - \alpha_{it})\right)} \]
 
@@
 
-\subsection{Posterior Specification for $\phi$}
+\subsection{Posterior Specification for $\phi_t$}
 
-\[p(\phi_k | \beta_t, z, w, b^2) \propto p(w | \phi_k, z) p(\phi_k | \beta_t)\]
+\[p(\phi_t | \beta_t, z, w, b^2) \propto p(w | \phi_t, z) p(\phi_t | \beta_t)\]
 
-\[= Mult(\pi(phi_{k,z})) N(\beta_t, b^2)\]
+\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(\pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, b^2)\]
 
-\[\propto \left(\prod_{i:z_i=k}^N \prod_{v=1}^V \frac{\phi_{k, v}^{I_{w_i}=v}}{\sum_v \phi_k}\right) \left(\exp{-\frac{1}{2}(\phi_k - \beta_t)^T(\phi_k - \beta_t)}\right) \]
+\[\propto \left(\prod_{k=1}^K \prod_{j=1}^{J_k} \frac{\phi_{kt}^{I_{w_j}=v}}{\sum_v \phi_{kt}}\right) \exp{\left(\sum_{k=1}^K(\phi_{kt} - \beta_t)^T(\phi_{kt} - \beta_t)\right)}\]
 

### 2014-07-08 gamma_mcmc.py
alpha gamma beta code

@@ -1,0 +1,35 @@
+import numpy as np
+
+
+def postBetaLog(phi, beta_t, beta_tn1):
+    """generates the log proposed value for a proposal beta_t"""
+
+    prior = np.dot((beta_t - beta_tn1).T, (beta_t - beta_tn1))
+    like = 0.0
+    for phi_k in phi:
+        like += np.dot((phi_k - beta_t).T, (phi_k - beta_t))
+    return like + prior
+
+
+def postAlphaLog(theta, alpha_it, gamma_i, alpha_tn1):
+    """generates the log proposed value for a proposal alpha_it"""
+
+    # NOTE: The set up on all these is important.  alpha_tn1 is a KxN matrix, where K is the number of topics and N is the number of agents.  gamma_i is a Nx1 array. alpha_tn1 is a Kx1 array.
+
+    prior = np.dot((alpha_it - np.squeeze(np.dot(alpha_tn1, gamma_i))).T, (alpha_it - np.squeeze(np.dot(alpha_tn1, gamma_i))))
+    like = 0.0
+    for theta_d in theta:
+        like += np.dot((theta_d - alpha_it).T, (theta_d - alpha_it))
+    return like + prior
+
+
+def postGammaLog(alpha_i, gamma_i, alpha_n1, mu):
+    """generates the log proposed value for a proposal gamma_i"""
+
+    # NOTE: alpha_n1 is a list of the PRIOR period values for alpha_t, alpha_i is a list of the current values for alpha_it
+
+    prior = np.dot((gamma_i - mu).T, (gamma_i - mu))
+    like = 0.0
+    for a_it, a_tn1 in zip(alpha_i, alpha_n1):
+        like += np.dot((a_it - np.squeeze(np.dot(a_tn1, gamma_i))).T, (a_it - np.squeeze(np.dot(a_tn1, gamma_i))))
+    return like + prior

### 2014-07-11 arxiv_scraper.py
fix source file

@@ -98,7 +98,7 @@ def writeArticleDictCSV(article, csv_f):
 def getArticles(article_url_f, url, t_sleep, output_csv, start_ind):
     """gets the articles from a list of urls"""
 
-    article_urls = cPickle.load(open(article_url_f, "rb"))
+    article_urls = open(article_url_f, "rb").read().split("\n")[:-1]
     ln = len(article_urls)
     t_1 = datetime.now()
     for i, a in enumerate(article_urls[start_ind:]):

### 2014-07-11 arxiv_scraper.py
ignore pdf

@@ -3,6 +3,7 @@ import cPickle
 import unicodecsv
 from datetime import datetime
 import requests
+# import slate
 import time
 
 
@@ -79,10 +80,10 @@ def getArticle(url, a_url):
     pdf_url = soup.find("div", {"class": "full-text"}).find("ul").find("li").find("a")["href"] 
     pdf.write(requests.get(url + pdf_url).content)
     pdf.close()
-    # extract the text from the pdf
-    input_ = open(f_name, "rb")
-    doc = slate.PDF(input_)
-    article_dict["text"] = doc
+    # # extract the text from the pdf
+    # input_ = open(f_name, "rb")
+    # doc = slate.PDF(input_)
+    # article_dict["text"] = doc
     return article_dict
 
 

### 2014-07-11 arxiv_scraper.py
rebuild scraper

@@ -72,14 +72,18 @@ def getArticle(url, a_url):
     article_dict["date"] = soup.find("div", {"class": "dateline"}).text
     article_dict["sub_hist"] = [a.text for a in
                                 soup.find("div", {"class": "submission-history"}).findAll("br")]
-    # write the pdf to the correct file
-    l_name = a_url.split("/")[-1]
-    article_dict["link"] = l_name
-    f_name = l_name + ".pdf"
-    pdf = open(f_name, "wb")
-    pdf_url = soup.find("div", {"class": "full-text"}).find("ul").find("li").find("a")["href"] 
-    pdf.write(requests.get(url + pdf_url).content)
-    pdf.close()
+    if soup.find("blockquote") is not None:
+        article_dict["abstract"] = soup.find("blockquote").text
+    else:
+        article_dict["abstract"] = None
+    # # write the pdf to the correct file
+    # l_name = a_url.split("/")[-1]
+    # article_dict["link"] = l_name
+    # f_name = l_name + ".pdf"
+    # pdf = open(f_name, "wb")
+    # pdf_url = soup.find("div", {"class": "full-text"}).find("ul").find("li").find("a")["href"] 
+    # pdf.write(requests.get(url + pdf_url).content)
+    # pdf.close()
     # # extract the text from the pdf
     # input_ = open(f_name, "rb")
     # doc = slate.PDF(input_)

### 2014-07-11 mcmc.jl
fix alpha and beta appendix

@@ -1,0 +1,8 @@
+using MCMC
+
+"""test data"""
+alpha = [[rand(K) for n in 1:N] for tt in 1:T]
+gamma = [rand(N) for n in 1:N]
+
+ex = quote
+    [[alpha_it ~ MvNormal(transpose(gamma_i * alpha_tn), delta2) for (alpha_it, gamma_i) in zip(alpha_t, gamma)] for (alpha_t, alpha_tn) in zip(alpha[2:], alpha[1:T-1])]

### 2014-07-11 test_julia.jl

@@ -1,0 +1,8 @@
+use MCMC
+
+modelxpr = quote
+    v ~ Normal(0, 1)
+    k ~ Normal(v, 1)
+end
+
+mymodel = model(modelxpr, k=ones(3))

### 2014-07-11 paper/paper.tex
fix alpha and beta appendix
take care of gamma
phi and theta

@@
 
-\[p(\beta_t | \phi, \beta_{t-1}, b^2, \sigma^2) \propto p(\phi | \beta_t) p(\beta_t | \beta_{t-1})\]
+\[p(\beta_t | \phi_t, \beta_{t-1}, b^2, \sigma^2) \propto \prod_{k=1}^K p(\phi_{kt} | \beta_t) p(\beta_t | \beta_{t-1})\]
 
-\[=  \prod_{k=1}^K N(\beta_t, b^2I) N(\beta_{t-1}, \sigma^2I)\]
+\[= \prod_{k=1}^K N(\phi_{kt};\beta_t, b^2) N(\beta_{t-1}, \sigma^2)\]
 
-\[\propto \exp{\left(\sum_{k=1}^K(\phi_k - \beta_{t})^T(\phi_k - \beta_{t}) + (\beta_{t} - \beta_{t-1})^T(\beta_{t} - \beta_{t-1})\right)}\]
+\[\propto N(\mu_{\beta t}, \Lambda_{\beta t})\]
 
-Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+\[\Lambda_{\beta t} = ((\sigma^2)^{-1} + k (b^2)^{-1})^{-1}\]
+
+\[\mu_{\beta t} = \Lambda_{\beta t} \left((\sigma^2)^{-1}\beta_{t-1} + k (b^2)^{-1} \sum_{k=1}^K \phi_{kt}\right) \]
 
@@
 
-\[p(\alpha_{it} | \theta, \text{\boldmath$\alpha$}_{t-1}, \gamma_i, a^2, \delta^2) \propto p(\theta | \alpha_{it}) p(\alpha_t | \text{\boldmath$\alpha$}, \gamma_i)\]
+\[p(\alpha_{it} | \theta_{it}, \text{\boldmath$\alpha$}_{t-1}, \gamma_i, a^2, \delta^2) \propto \prod_{k=1}^K p(\phi_{kt} | \beta_t) p(\beta_t | \beta_{t-1})\]
 
-\[= \prod_{d=1}^{D_i} N(\alpha_{it}, a^2I) N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)\]
+\[= \prod_{d=1}^{D_i} N(\theta_{dit};\alpha_{it}, a^2) N(\text{\boldmath$\alpha$}_{t-1}\gamma_i, \delta^2)\]
 
-\[\propto \exp{\left(\sum_{d=1}^{D_i}(\theta_d - \alpha_{it})^T(\theta_d - \alpha_{it}) + (\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)\right)}\]
+\[\propto N(\mu_{\alpha i t}, \Lambda_{\alpha i t})\]
 
-Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+\[\Lambda_{\alpha i t} = ((\delta^2)^{-1} + d_i (a^2)^{-1})^{-1}\]
+
+\[\mu_{\alpha i t} = \Lambda_{\alpha i t} \left((\delta^2)^{-1}\text{\boldmath$\alpha$}_{t-1} \gamma_i + d_i (a^2)^{-1} \sum_{d=1}^{D_i} \theta_{dit}\right) \]
 
@@
 
-\[p(\gamma_i | \alpha_{it}, \text{\boldmath$\alpha$}_{t-1}, \mu, \xi^2) \propto p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \mu, \xi^2)\]
+\[p(\gamma_i | \text{\boldmath$\alpha$}_{i}, \text{\boldmath$\alpha$}_{-1}, \eta, \xi^2) \propto p(\text{\boldmath$\alpha$}_i | \text{\boldmath$\alpha$}_{-1}, \gamma_i, \delta^2) p(\gamma_i | \eta, \xi^2)\]
 
-\[= \prod_{t=2}^T N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)N(\mu, \xi^2)\]
+\[= N(\text{\boldmath$\alpha$}_{i};\text{\boldmath$\alpha$}_{-1}^T \gamma_i, \delta^2)N(\eta, \xi^2)\]
 
-\[\propto \exp{\left(\sum_{t=2}^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i) + (\gamma_i - \mu)^T(\gamma_i - \mu)\right)}\]
+\[\propto N(\mu_{\gamma i}, \Lambda_{\gamma i})\]
 
-Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+\[\Lambda_{\gamma i} = \left((\xi^2)^{-1} + \text{\boldmath$\alpha$}_{-1}^T(\delta^2)^{-1}\text{\boldmath$\alpha$}_{-1}\right)^{-1}\]
+
+\[\mu_{\gamma i} = \Lambda_{\gamma i} \left((\xi^2)^{-1} \eta + \text{\boldmath$\alpha$}_{-1}^T(\delta^2)^{-1}\text{\boldmath$\alpha$}_{i}\right)\]
 
@@
 
-\[= \prod_{d=1}^D \prod_{j=1}^{J_d} Mult(\pi(\theta_{dit}))\prod_{d=1}^D N(\alpha_{it}, \delta^2I)\]
+\[= \prod_{d=1}^{D_i} \prod_{j=1}^{J_d} Mult(z_{jdit}; \pi(\theta_{dit}))\prod_{d=1}^{D_i} N(\alpha_{it}, \delta^2I)\]
 
-\[\propto \left(\prod_{d=1}^D \prod_{j=1}^{J_d} \frac{\theta_{dit}^{I_{z_j}=k}}{\sum_k \theta_{dit}}\right) \exp{\left(\sum_{d=1}^D(\theta_{dit} - \alpha_{it})^T(\theta_{dit} - \alpha_{it})\right)} \]
-
-Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+Since this doesn't have a standard form we use a slice sampler to sample from the full conditional.
 
@@
 
-\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(\pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, b^2)\]
+\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(w_{jkt}; \pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, b^2)\]
 
-\[\propto \left(\prod_{k=1}^K \prod_{j=1}^{J_k} \frac{\phi_{kt}^{I_{w_j}=v}}{\sum_v \phi_{kt}}\right) \exp{\left(\sum_{k=1}^K(\phi_{kt} - \beta_t)^T(\phi_{kt} - \beta_t)\right)}\]
-
-Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.
+Since this doesn't have a standard form we use a slice sampler to sample from the full conditional.
 

### 2014-07-12 paper/paper.tex
local changes
finish fixing posteriors
fix full conditional

@@
 
-\[p(\gamma_i | \mu, \xi^2) = N(\mu, \xi^2I)\]
+\[p(\gamma_i | \mu, \xi^2) = N(\eta, \xi^2)\]
 
-\[p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}. \gamma_i, \delta^2) = N(\text{\boldmath$\alpha$}^T_{t-1} \gamma_i, \delta^2I)\]
+\[p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) = N(\text{\boldmath$\alpha$}^T_{t-1} \gamma_i, \delta^2)\]
 
-\[p(\beta_t | \beta_{t-1}, \sigma^2) = N(\beta_{t-1}, \sigma^2I)\]
+\[p(\beta_t | \beta_{t-1}, \sigma^2) = N(\beta_{t-1}, \sigma^2)\]
 
-\[p(\theta | \alpha_{it}, a^2) = N(\alpha_{it}, a^2I)\]
+\[p(\theta | \alpha_{it}, a^2) = N(\alpha_{it}, a^2)\]
 
-\[p(\phi | \beta_t, b^2) = N(\beta_t, b^2I)\]
+\[p(\phi | \beta_t, b^2) = N(\beta_t, b^2)\]
+
+\[p(a^2 | \nu_0, \tau_0) = IW(\nu_0, \tau_0)\]
+
+\[p(b^2 | \nu_1, \tau_1) = IW(\nu_1, \tau_1)\]
 
@@
 
-\[p(\theta, \phi, \gamma_i, \alpha_{it}, \beta_t, z | w) \propto p(w | \phi, z) p(\phi |  \beta_t, b^2)  p(z | \theta)  p(\beta_t | \beta_{t-1}, \sigma^2) p(\theta | \alpha_{it}, a^2) p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \mu, xi^2)\]
+\[p(\theta, \phi, \gamma, \alpha, \beta, z | w) \propto \prod_{t=1}^T \prod_{i=1}^N \prod_{d=1}^{D_i} \prod_{j=1}^{J_d} \prod_{k=1}^K p(w_{jit} | \phi_k, z_{jit}) p(\phi_k | \beta_t, b^2) p(b^2 | \nu_1, \tau_1) p(z_{jit} | \theta_{dit}) p(\beta_t | \beta_{t-1}, \sigma^2) p(\theta_{dit} | \alpha_{it}, a^2) p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \eta, xi^2)\]
 
@@
 
-\[= \frac{\theta_{it}^{I_{z_{jit}}=k}}{\sum_k \theta_{it}} \frac{\phi_{kt}^{I_{w_j}=v}}{\sum_v \phi_{kt}}\]
+\[= \frac{\theta_{it}^{I_{z_{jit}}=k}}{\sum_k \theta_{it}} \frac{\phi_{t}^{I_{w_{jit}}=v}}{\sum_v \phi_{kt}}\]
 
@@
 
+\subsection{Posterior Specification for $b^2$}
+
+\[p(b^2|\beta,\phi) \propto \prod_{t=1}^T \prod_{k=1}^K p(\phi_{kt} | \beta_t, b^2)p(b^2 | \nu_0, \tau_0) \]
+
+\[= \prod_{t=1}^T \prod_{k=1}^K N(\phi_{kt};\beta_t, b^2)IW(\nu_0, \tau_0)\]
+
+\[\propto IW\left(\nu_0 + TK, \left(\tau_0 + \sum_{t=1}^T \sum_{k=1}^K (\phi_{kt} - \beta_t)(\phi_{kt} - \beta_t)^T\right)^{-1}\right)\]
+
 \subsection{Posterior Specification for $\alpha_{it}$}
@@
 \[\mu_{\alpha i t} = \Lambda_{\alpha i t} \left((\delta^2)^{-1}\text{\boldmath$\alpha$}_{t-1} \gamma_i + d_i (a^2)^{-1} \sum_{d=1}^{D_i} \theta_{dit}\right) \]
+
+\subsection{Posterior Specification for $a^2$}
+
+\[p(a^2|\alpha,\theta) \propto \prod_{t=1}^T \prod_{i=1}^N \prod_{d=1}^{D_i} p(\theta_{dit} | \alpha_{it}, a^2)p(a^2 | \nu_1, \tau_1) \]
+
+\[= \prod_{t=1}^T \prod_{i=1}^N \prod_{k=1}^K N(\theta_{dit};\alpha_{it}, a^2)IW(\nu_1, \tau_1)\]
+
+This needs to be fixed
+
+\[\propto IW\left(\nu_1 + TND, \left(\tau_0 + \sum_{t=1}^T \sum_{i=1}^N \sum_{d=1}^{D_i} (\theta_{dit} - \alpha_{it})(\theta_{dit} - \alpha_{dit})^T\right)^{-1}\right)\]
 

### 2014-07-15 arxiv_scraper.py
gamma code basics

@@ -70,8 +70,7 @@ def getArticle(url, a_url):
     article_dict["authors"] = [a.text for a in
                                soup.find("div", {"class": "authors"}).findAll("a")]
     article_dict["date"] = soup.find("div", {"class": "dateline"}).text
-    article_dict["sub_hist"] = [a.text for a in
-                                soup.find("div", {"class": "submission-history"}).findAll("br")]
+    article_dict["sub_hist"] = soup.find("div", {"class": "submission-history"}).text
     if soup.find("blockquote") is not None:
         article_dict["abstract"] = soup.find("blockquote").text
     else:
@@ -110,6 +109,7 @@ def getArticles(article_url_f, url, t_sleep, output_csv, start_ind):
         article = getArticle(url, a)
         writeArticleDictCSV(article, output_csv)
         print start_ind + i, (start_ind + i) * 100. / ln, datetime.now() - t_1
+        time.sleep(t_sleep)
 
 
 def fullRun(url, t_sleep, url_f, output_f, backup_f, start_ind, urls=True):

### 2014-07-15 gamma_mcmc.py

@@ -1,35 +1,25 @@
-import numpy as np
+from numpy import *
+
+def processWords(word):
+    """returns vector of letters in vocab"""
+
+    return
 
 
-def postBetaLog(phi, beta_t, beta_tn1):
-    """generates the log proposed value for a proposal beta_t"""
+def fullRun(N, K, T, V, iterations, graph, xi2, delta2): 
 
-    prior = np.dot((beta_t - beta_tn1).T, (beta_t - beta_tn1))
-    like = 0.0
-    for phi_k in phi:
-        like += np.dot((phi_k - beta_t).T, (phi_k - beta_t))
-    return like + prior
+    # initalize values
+    gamma = array([[1. / N for i in range(N)] for i in range(N)])
+    alpha = array([[[1. for k in range(K)] for t in range(T)] for i in range(N)])
+    beta = array([[1. for v in range(V)] for t in range(T)])
+    phi = array([[[1. for v in range(V)] for k in range(K)] for t in range(T)])
+    theta = array([[[[1. for d in range(len(docs))] for docs in period] for period in node] for node in graph])
 
+    for j in iterations:
+        for gamma_i, alpha_i, theta_i in zip(gamma, alpha, theta):
+            # Gibbs sampling for gamma i
+            lambda_gi = linalg.inv(linalg.inv(xi2) + transpose(alpha_n1) * linalg.inv(delta2) * alpha_n1)
+            mu_gi = lambda_gi * (linalg.inv(xi2) * eta + transpose(alpha_n1) * linalg.inv(delta2) * alpha_i)
+            gamma_i = random.multivariate_normal(mu_gi, lambda_gi)
+            for alpha_it, 
 
-def postAlphaLog(theta, alpha_it, gamma_i, alpha_tn1):
-    """generates the log proposed value for a proposal alpha_it"""
-
-    # NOTE: The set up on all these is important.  alpha_tn1 is a KxN matrix, where K is the number of topics and N is the number of agents.  gamma_i is a Nx1 array. alpha_tn1 is a Kx1 array.
-
-    prior = np.dot((alpha_it - np.squeeze(np.dot(alpha_tn1, gamma_i))).T, (alpha_it - np.squeeze(np.dot(alpha_tn1, gamma_i))))
-    like = 0.0
-    for theta_d in theta:
-        like += np.dot((theta_d - alpha_it).T, (theta_d - alpha_it))
[…]

### 2014-07-15 gamma_mcmc.py
alpha posterior

@@ -6,6 +6,27 @@ def processWords(word):
     return
 
 
+def alphaPost(alpha_n1, gamma_i, delta2, a2 theta_dit, I, d_it):
+    """generates the full conditional for alpha_it
+    
+    delta2: scalar
+    a2: scalar
+    I: NxN identity matrix
+    d_it: scalar, the number of documents for a given node in a given period
+    alpha_it: NxK matrix of proportions for each node.  Each row is a node and each column is a proportion
+    gamma_i: Nx1 vector, each element is a weight for that node
+    theta_dit: DxK matrix of draws for each document.  Each row is the document and each column is the topic
+
+    """
+
+    # NOTE: multiplying lambda_ait * ... may not have the desired effect, this likely will need to be
+    # fixed in testing
+
+    lambda_ait = linalg.inv(1 / delta2 * I + d_it / a2 * I)
+    mu_ait = lambda_ait * (1 / delta2 * I * dot(alpha_it * gamma_i) + d_it / a2 * I *  sum(theta_dit))
+    return random.multivariate_normal(mu_ait, lambda_ait)
+
+
 def fullRun(N, K, T, V, iterations, graph, xi2, delta2): 
 
     # initalize values

### 2014-07-16 gamma_mcmc.py
posterior beta

@@ -6,16 +6,17 @@ def processWords(word):
     return
 
 
-def alphaPost(alpha_n1, gamma_i, delta2, a2 theta_dit, I, d_it):
+def alphaPost(alpha_n1, gamma_i, delta2, a2 theta_it, I, d_it):
     """generates the full conditional for alpha_it
     
     delta2: scalar
     a2: scalar
-    I: NxN identity matrix
+    I: KxK identity matrix
     d_it: scalar, the number of documents for a given node in a given period
     alpha_it: NxK matrix of proportions for each node.  Each row is a node and each column is a proportion
     gamma_i: Nx1 vector, each element is a weight for that node
-    theta_dit: DxK matrix of draws for each document.  Each row is the document and each column is the topic
+    dot(alpha_it, gamma_i): Kx1 vector
+    theta_it: DxK matrix of draws for each document.  Each row is the document and each column is the topic
 
     """
 
@@ -23,8 +24,25 @@ def alphaPost(alpha_n1, gamma_i, delta2, a2 theta_dit, I, d_it):
     # fixed in testing
 
     lambda_ait = linalg.inv(1 / delta2 * I + d_it / a2 * I)
-    mu_ait = lambda_ait * (1 / delta2 * I * dot(alpha_it * gamma_i) + d_it / a2 * I *  sum(theta_dit))
+    mu_ait = lambda_ait * (1 / delta2 * I * dot(alpha_it, gamma_i) + d_it / a2 * I *  sum(theta_dit))
     return random.multivariate_normal(mu_ait, lambda_ait)
+
+
+def betaPost(beta_n1, sigma2, b2, phi_t, I, k):
+    """generates the full conditional for beta_t
+
+    sigma2: scalar
+    b2: scalar
+    I: VxV identity matrix
+    k: scalar, the number of topics
+    beta_n1: Vx1 vector
+    phi_t: KxV matrix of proportions for each topic for each word.
+
+    """
+
+    lambda_bit = linalg.inv(1 / sigma2 * I + k / b2 * I)
+    mu_bit = lambda_bit * (1 / sigma2 * I * beta_n1 + k / b2 * I * sum(phi_t))
+    return random.multivariate_normal(mu_bit, lambda_bit)
 
 
 def fullRun(N, K, T, V, iterations, graph, xi2, delta2): 

### 2014-07-17 gamma_mcmc.py
add gamma code

@@ -45,6 +45,18 @@ def betaPost(beta_n1, sigma2, b2, phi_t, I, k):
     return random.multivariate_normal(mu_bit, lambda_bit)
 
 
+def gammaPost(alpha_i, alpha_n, xi2, mu, delta2, I):
+    """generates the full conditional for gamma_i
+
+    
+
+    """
+
+    lambda_gi = linalg.inv(1 / xi2 * I + dot(sum(alpha_n), sum(alpha_n) / delta2))
+    mu_gi = lambda_gi * (eta / xi2 + dot(sum(alpha_n), sum(alpha_i)) / delta2)
+    return random.multivariate_normal(mu_gi, lambda_gi)
+
+
 def fullRun(N, K, T, V, iterations, graph, xi2, delta2): 
 
     # initalize values

### 2014-07-17 gamma_mcmc.py
add gamma code

@@ -13,18 +13,17 @@ def alphaPost(alpha_n1, gamma_i, delta2, a2 theta_it, I, d_it):
     a2: scalar
     I: KxK identity matrix
     d_it: scalar, the number of documents for a given node in a given period
-    alpha_it: NxK matrix of proportions for each node.  Each row is a node and each column is a proportion
+    alpha_n1: NxK matrix of proportions for each node.  Each row is a node and each column is a proportion
     gamma_i: Nx1 vector, each element is a weight for that node
-    dot(alpha_it, gamma_i): Kx1 vector
+    dot(alpha_n1, gamma_i): Kx1 vector
     theta_it: DxK matrix of draws for each document.  Each row is the document and each column is the topic
+    mu_ait: Kx1 vector
 
     """
 
-    # NOTE: multiplying lambda_ait * ... may not have the desired effect, this likely will need to be
-    # fixed in testing
 
     lambda_ait = linalg.inv(1 / delta2 * I + d_it / a2 * I)
-    mu_ait = lambda_ait * (1 / delta2 * I * dot(alpha_it, gamma_i) + d_it / a2 * I *  sum(theta_dit))
+    mu_ait = dot(lambda_ait, (1 / delta2 * I * dot(alpha_n1, gamma_i) + d_it / a2 * I *  sum(theta_dit)))
     return random.multivariate_normal(mu_ait, lambda_ait)
 
 
@@ -37,23 +36,34 @@ def betaPost(beta_n1, sigma2, b2, phi_t, I, k):
     k: scalar, the number of topics
     beta_n1: Vx1 vector
     phi_t: KxV matrix of proportions for each topic for each word.
-
+    mu_bit: Vx1 vector
+    
     """
 
     lambda_bit = linalg.inv(1 / sigma2 * I + k / b2 * I)
-    mu_bit = lambda_bit * (1 / sigma2 * I * beta_n1 + k / b2 * I * sum(phi_t))
+    mu_bit = dot(lambda_bit, (1 / sigma2 * I * beta_n1 + k / b2 * I * sum(phi_t)))
     return random.multivariate_normal(mu_bit, lambda_bit)
 
 
 def gammaPost(alpha_i, alpha_n, xi2, mu, delta2, I):
     """generates the full conditional for gamma_i
 
-    
+    xi2: scalar
+    delta2: scalar
[…]

### 2014-07-17 gamma_mcmc.py
Update gamma_mcmc.py

@@ -75,12 +75,19 @@ def fullRun(N, K, T, V, iterations, graph, xi2, delta2):
     beta = array([[1. for v in range(V)] for t in range(T)])
     phi = array([[[1. for v in range(V)] for k in range(K)] for t in range(T)])
     theta = array([[[[1. for d in range(len(docs))] for docs in period] for period in node] for node in graph])
+    
+    # initalize storage
+    gamma_s = array([[[1. / N for i in range(N)] for i in range(N)] for s in range(S)])
+    alpha_s = array([[[[1. for k in range(K)] for t in range(T)] for i in range(N)] for s in range(S)])
+    beta_s = array([[[1. for v in range(V)] for t in range(T)] for s in range(S)])
+    phi_s = array([[[[1. for v in range(V)] for k in range(K)] for t in range(T)] for s in range(S)])
+    theta_s = array([[[[[1. for d in range(len(docs))] for docs in period] for period in node] for node in graph] for s in range(S)])
+    
+    
 
     for j in iterations:
+        alpha_n = genPevAlpha(alpha)
         for gamma_i, alpha_i, theta_i in zip(gamma, alpha, theta):
-            # Gibbs sampling for gamma i
-            lambda_gi = linalg.inv(linalg.inv(xi2) + transpose(alpha_n1) * linalg.inv(delta2) * alpha_n1)
-            mu_gi = lambda_gi * (linalg.inv(xi2) * eta + transpose(alpha_n1) * linalg.inv(delta2) * alpha_i)
-            gamma_i = random.multivariate_normal(mu_gi, lambda_gi)
-            for alpha_it, 
+            
+            
 

### 2014-07-17 gamma_mcmc.py
full run code

@@ -1,4 +1,5 @@
 from numpy import *
+from datetime import datetime
 
 def processWords(word):
     """returns vector of letters in vocab"""
@@ -23,7 +24,7 @@ def alphaPost(alpha_n1, gamma_i, delta2, a2 theta_it, I, d_it):
 
 
     lambda_ait = linalg.inv(1 / delta2 * I + d_it / a2 * I)
-    mu_ait = dot(lambda_ait, (1 / delta2 * I * dot(alpha_n1, gamma_i) + d_it / a2 * I *  sum(theta_dit)))
+    mu_ait = dot(lambda_ait, (1 / delta2 * I * dot(alpha_n1, gamma_i) + d_it / a2 * I *  sum(theta_it)))
     return random.multivariate_normal(mu_ait, lambda_ait)
 
 
@@ -67,7 +68,15 @@ def gammaPost(alpha_i, alpha_n, xi2, mu, delta2, I):
     return random.multivariate_normal(mu_gi, lambda_gi)
 
 
-def fullRun(N, K, T, V, iterations, graph, xi2, delta2): 
+def genPrevAlpha(alpha, T, N):
+    """gets the previous alpha values"""
+
+    # this essentially transposes the N and T values without changing the inner values
+    alpha_n = array([[alpha[i, t] for i in range(N)] for t in range(T-1)])
+    return alpha_n
+
+
+def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2): 
 
     # initalize values
     gamma = array([[1. / N for i in range(N)] for i in range(N)])
@@ -77,17 +86,60 @@ def fullRun(N, K, T, V, iterations, graph, xi2, delta2):
     theta = array([[[[1. for d in range(len(docs))] for docs in period] for period in node] for node in graph])
     
     # initalize storage
-    gamma_s = array([[[1. / N for i in range(N)] for i in range(N)] for s in range(S)])
-    alpha_s = array([[[[1. for k in range(K)] for t in range(T)] for i in range(N)] for s in range(S)])
-    beta_s = array([[[1. for v in range(V)] for t in range(T)] for s in range(S)])
-    phi_s = array([[[[1. for v in range(V)] for k in range(K)] for t in range(T)] for s in range(S)])
-    theta_s = array([[[[[1. for d in range(len(docs))] for docs in period] for period in node] for node in graph] for s in range(S)])
+    gamma_s = array([[[nan for i in range(N)] for i in range(N)] for s in range(S)])
[…]

### 2014-07-17 gamma_mcmc.py
logit normal

@@ -68,6 +68,24 @@ def gammaPost(alpha_i, alpha_n, xi2, mu, delta2, I):
     return random.multivariate_normal(mu_gi, lambda_gi)
 
 
+def logitNormalSampler(z, theta_dit, theta_it, alpha_it, a2, I):
+    """generates a augmented variable sample for theta
+
+    """
+
+    un_l = array([])
+    un_u = array([])
+    for z_w in z:
+        if z_w == theta_it:
+            un_l.append(random.uniform(0, exp(theta_dit) / exp(sum(theta_it))))
+        else:
+            un_u.append(random.uniform(exp(theta_dit) / exp(sum(theta_it)), 1))
+    mx_mn = max(un_l)
+    mn_mx = min(un_u)
+    return truncatedMVN(mx_mn, mn_mx, alpha_it, a2 * I)
+
+
+
 def genPrevAlpha(alpha, T, N):
     """gets the previous alpha values"""
 
@@ -119,7 +137,7 @@ def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2):
                     w_it = len(graph[i, t, d])
 
                     theta_s[s, i, t, d] = theta[i, t, d]
-                    theta[i, t, d] = thetaPost(z[i, t, d], alpha[i, t], delta2, I)
+                    theta[i, t, d] = logitNormalSamplert(z[i, t, d], theta[i, t, d], theta[i, t], alpha[i, t], a2, I)
 
                     for w in range(w_it):
 
@@ -138,7 +156,7 @@ def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2):
             for k in range(K):
 
                 phi_s[s, t, k] = phi[t, k]
-                phi[t, k] = phiPost(vocab[t, k], beta[t], sigma2, I)
+                phi[t, k] = logitNormalSampler(vocab[t, k], phi[t, k], phi[t], beta[t], b2, I)
 
         print datetime.now() - t_1, (s * 100.) / S
 

### 2014-07-18 gamma_mcmc.py
alphaPost test and fix

@@ -7,24 +7,43 @@ def processWords(word):
     return
 
 
-def alphaPost(alpha_n1, gamma_i, delta2, a2 theta_it, I, d_it):
+def alphaPost(alpha_n1, gamma_i, delta2, a2, theta_it, I, d_it):
     """generates the full conditional for alpha_it
     
-    delta2: scalar
-    a2: scalar
-    I: KxK identity matrix
-    d_it: scalar, the number of documents for a given node in a given period
-    alpha_n1: NxK matrix of proportions for each node.  Each row is a node and each column is a proportion
-    gamma_i: Nx1 vector, each element is a weight for that node
-    dot(alpha_n1, gamma_i): Kx1 vector
-    theta_it: DxK matrix of draws for each document.  Each row is the document and each column is the topic
-    mu_ait: Kx1 vector
+    * delta2: scalar
+    * a2: scalar
+    * I: KxK identity matrix
+    * d_it: scalar, the number of documents for a given node in a given
+    period
+    * alpha_n1: NxK matrix of proportions for each node.  Each row is a
+    node and each column is a proportion
+    * gamma_i: Nx1 vector, each element is a weight for that node
+    * theta_it: DxK matrix of draws for each document.  Each row is the
+    document and each column is the topic
+    * mu_ait: Kx1 vector
+
+    NOTES:
+
+    * theta_it.sum(axis=0) sums all the columns so you get a Kx1 vector
+    that is the sum of thetas over the documents
+    * dot(alpha_n1, gamma_i) is a Kx1 vector for the "mean".
+    * 1 / delta2 * I is a KxK diagonal matrix with 1 / delta2 in the diagonal
+    * d_it / a2 * I is a KxK diagonal matrix with d_it / a2 in the diagonal
+    * dot(transpose(1 / delta2 * I), dot(transpose(alpha_n1), gamma_i)) is
+    a Kx1 vector for the prior
+    * dot(transpose(d_it / a2 * I), theta_it.sum(axis=0)) is a Kx1 vector
+    for the data
+
+    * lambda_ait is a KxK matrix of the covariance
+    * mu_ait is a Kx1 vector for the mean
 
     """
 
-
     lambda_ait = linalg.inv(1 / delta2 * I + d_it / a2 * I)
[…]

### 2014-07-18 test_mcmc.py

@@ -1,0 +1,16 @@
+import gamma_mcmc
+from numpy import *
+
+# alphaPost test
+
+alpha_n1 = random.randint(1, 20, size=(20, 10))
+gamma_i = random.rand(20)
+delta2 = 10.
+a2 = 10.
+theta_it = 4 * random.randn(5, 10) + 25
+I = identity(10)
+d_it = 5
+
+res = gamma_mcmc.alphaPost(alpha_n1, gamma_i, delta2, a2, theta_it, I, d_it)
+
+# betaPost test

### 2014-07-18 gamma_mcmc.py
fix beta

@@ -50,18 +50,28 @@ def alphaPost(alpha_n1, gamma_i, delta2, a2, theta_it, I, d_it):
 def betaPost(beta_n1, sigma2, b2, phi_t, I, k):
     """generates the full conditional for beta_t
 
-    sigma2: scalar
-    b2: scalar
-    I: VxV identity matrix
-    k: scalar, the number of topics
-    beta_n1: Vx1 vector
-    phi_t: KxV matrix of proportions for each topic for each word.
-    mu_bit: Vx1 vector
+    * sigma2: scalar
+    * b2: scalar
+    * I: VxV identity matrix
+    * k: scalar, the number of topics
+    * beta_n1: Vx1 vector
+    * phi_t: KxV matrix of proportions for each topic for each word.
+    * mu_bit: Vx1 vector
     
+    NOTES:
+
+    * phi_t.sum(axis=0) sums all the columns so you get a Vx1 vector.
+    The columns in this case are the topics.  There is a phi_tk for
+    each topic.
+    * See alphaPost notes.  It is basically the same.
+
     """
 
     lambda_bit = linalg.inv(1 / sigma2 * I + k / b2 * I)
-    mu_bit = dot(lambda_bit, (1 / sigma2 * I * beta_n1 + k / b2 * I * sum(phi_t)))
+    mu_bit = dot(lambda_bit, (dot(transpose(1 / sigma2 * I),
+                                  beta_n1)
+                              + dot(transpose(k / b2 * I),
+                                    phi_t.sum(axis=0))))
     return random.multivariate_normal(mu_bit, lambda_bit)
 
 

### 2014-07-18 test_mcmc.py

@@ -11,6 +11,15 @@ theta_it = 4 * random.randn(5, 10) + 25
 I = identity(10)
 d_it = 5
 
-res = gamma_mcmc.alphaPost(alpha_n1, gamma_i, delta2, a2, theta_it, I, d_it)
+alpha_r = gamma_mcmc.alphaPost(alpha_n1, gamma_i, delta2, a2, theta_it, I, d_it)
 
 # betaPost test
+
+beta_n1 = random.randint(1, 20, size=200)
+sigma2 = 10.
+b2 = 10.
+phi_t = 4 * random.randn(10, 200) + 25
+I = identity(200)
+k = 10
+
+beta_r = gamma_mcmc.betaPost(beta_n1, sigma2, b2, phi_t, I, k)

### 2014-07-18 gamma_mcmc.py
fix gamma

@@ -40,10 +40,10 @@ def alphaPost(alpha_n1, gamma_i, delta2, a2, theta_it, I, d_it):
     """
 
     lambda_ait = linalg.inv(1 / delta2 * I + d_it / a2 * I)
-    mu_ait = dot(lambda_ait, (dot(transpose(1 / delta2 * I),
-                                  dot(transpose(alpha_n1), gamma_i))
-                              + dot(transpose(d_it / a2 * I),
-                                    theta_it.sum(axis=0))))
+    mu_ait = dot(transpose(lambda_ait), (dot(transpose(1 / delta2 * I),
+                                             dot(transpose(alpha_n1), gamma_i))
+                                         + dot(transpose(d_it / a2 * I),
+                                               theta_it.sum(axis=0))))
     return random.multivariate_normal(mu_ait, lambda_ait)
 
 
@@ -68,32 +68,44 @@ def betaPost(beta_n1, sigma2, b2, phi_t, I, k):
     """
 
     lambda_bit = linalg.inv(1 / sigma2 * I + k / b2 * I)
-    mu_bit = dot(lambda_bit, (dot(transpose(1 / sigma2 * I),
-                                  beta_n1)
-                              + dot(transpose(k / b2 * I),
-                                    phi_t.sum(axis=0))))
+    mu_bit = dot(transpose(lambda_bit), (dot(transpose(1 / sigma2 * I),
+                                             beta_n1)
+                                         + dot(transpose(k / b2 * I),
+                                               phi_t.sum(axis=0))))
     return random.multivariate_normal(mu_bit, lambda_bit)
 
 
-def gammaPost(alpha_i, alpha_n, xi2, mu, delta2, I):
+def gammaPost(alpha_i, alpha_n, xi2, eta, delta2, I):
     """generates the full conditional for gamma_i
 
-    xi2: scalar
-    delta2: scalar
-    I: KxK identity matrix
-    alpha_n: Tx(NXK) matrix of alpha_it-1 matricies.  alpha_it-1 is an NxK matrix of proportions for each node.
-    Each row is a node and each column is a proportion
-    alpha_i: Tx(Kx1) matrix of alpha_it values.  alpha_it is a vector of the topic proportions for the ith node.
-    gamma_i: Nx1 vector, each element is a weight for that node
-    dot(sum(alpha_n), sum(alpha_n)): KxK matrix
[…]

### 2014-07-18 test_mcmc.py

@@ -23,3 +23,15 @@ I = identity(200)
 k = 10
 
 beta_r = gamma_mcmc.betaPost(beta_n1, sigma2, b2, phi_t, I, k)
+
+# gammaPost test
+
+alpha_i = random.randint(1, 20, size=(15, 10))
+alpha_n = random.randint(1, 20, size=(15, 20, 10))
+xi2 = 10.
+eta = random.rand(20)
+delta2 = 10.
+I = identity(20)
+
+gamma_r = gamma_mcmc.gammaPost(alpha_i, alpha_n, xi2, eta, delta2, I)
+

### 2014-07-18 gamma_mcmc.py
local changes

@@ -188,7 +188,7 @@ def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2):
                     w_it = len(graph[i, t, d])
 
                     theta_s[s, i, t, d] = theta[i, t, d]
-                    theta[i, t, d] = logitNormalSamplert(z[i, t, d], theta[i, t, d], theta[i, t], alpha[i, t], a2, I)
+                    theta[i, t, d] = logitNormalSampler(z[i, t, d], theta[i, t, d], theta[i, t], alpha[i, t], a2, I)
 
                     for w in range(w_it):
 

### 2014-07-19 gamma_mcmc.py
fix logit normal

@@ -94,7 +94,7 @@ def gammaPost(alpha_i, alpha_n, xi2, eta, delta2, I):
     * eta: Nx1 vector, the prior for gamma_i
     * mu_gi: Nx1 vector
 
-    Notes:
+    NOTES:
 
     * The only thing wierd here is the transposes.  Just think that alpha_n
     and alpha_i were already transposed before being fed in.
@@ -117,22 +117,24 @@ def zPost(theta_itd, w, phi_tk):
     return
 
 
-def logitNormalSampler(z, theta_dit, theta_it, alpha_it, a2, I):
+def logitNormalSampler(z, theta_dit, alpha_it, a2, I):
     """generates a augmented variable sample for theta
 
     """
 
-    un_l = array([])
-    un_u = array([])
-    for z_w in z:
-        if z_w == theta_it:
-            un_l.append(random.uniform(0, exp(theta_dit) / exp(sum(theta_it))))
-        else:
-            un_u.append(random.uniform(exp(theta_dit) / exp(sum(theta_it)), 1))
-    mx_mn = max(un_l)
-    mn_mx = min(un_u)
-    return truncatedMVN(mx_mn, mn_mx, alpha_it, a2 * I)
-
+    theta_ditp = array([])
+    for i, theta_kdit in enumerate(theta_dit):
+        un_l = array([])
+        un_u = array([])
+        for z_w in z:
+            if z_w[i] == 1:
+                un_l.append(random.uniform(0, exp(theta_kdit) / exp(sum(theta_dit))))
+            else:
+                un_u.append(random.uniform(exp(theta_kdit) / exp(sum(theta_dit)), 1))
+        mx_mn = max(un_l)
+        mn_mx = min(un_u)
+        theta_ditp.append(stats.truncnorm.ppf())
+    return theta_ditp
 
 
 def genPrevAlpha(alpha, T, N):

### 2014-07-19 test_mcmc.py

@@ -35,3 +35,29 @@ I = identity(20)
 
 gamma_r = gamma_mcmc.gammaPost(alpha_i, alpha_n, xi2, eta, delta2, I)
 
+
+# phi post test
+
+vocab = zeros((30, 200))
+for i, j in enumerate(random.randint(0, 200, size=(30))):
+    vocab[i, j] = 1
+phi_kt = 4 * random.randn(200) + 25
+phi_t = 4 * random.randn(10, 200) + 25
+beta_t = random.randint(1, 20, size=(200))
+b2 = 10.
+I = identity(200)
+
+phi_kt = gamma_mcmc.logitNormalSampler(vocab, phi_kt, phi_t, beta_t, b2, I)
+
+# theta post test
+
+z = zeros((30, 10))
+for i, j in enumerate(random.randint(0, 10, size=(30))):
+    z[i, j] = 1
+theta_dit = 4 * random.randn(10) + 25
+theta_it = 4 * random.randn(5, 10) + 25
+alpha_it = random.randint(1, 20, size=(10))
+a2 = 10.
+I = identity(10)
+
+theta_dit = gamma_mcmc.logitNormalSampler(z, theta_dit, theta_it, alpha_it, a2, I)

### 2014-07-19 gamma_mcmc.py
Fix logit normal

@@ -117,8 +117,31 @@ def zPost(theta_itd, w, phi_tk):
     return
 
 
-def logitNormalSampler(z, theta_dit, alpha_it, a2, I):
-    """generates a augmented variable sample for theta
+def logitNormalSampler(z, theta_dit, alpha_it, a2):
+    """generates a augmented variable sample for theta/phi, this is a general
+    function since they both have the same form.
+    
+    * z: WxK matrix.  This is a vector of the topics chosen for each of the W
+    words.
+    * theta_dit: Kx1 vector.  This is an array of each of the proportions
+    for the given document.  The result of this function is just an updated
+    version of this.
+    * alpha_it: Kx1 vector.  This is the underlying proportions.
+    * a2: scalar.
+    
+    NOTES:
+    
+    * This all works the same for the phis.  Where the thetas use documents,
+    phis use topics, where thetas use topics phis use vocabulary.
+    
+    In the phi case:
+    
+    * w: WxV matrix.  This is just a matrix of the words, each word is a location
+    in a vocab vector.
+    * phi_kt.  Vx1 vector.  This is a vector of the proportion for each word
+    for the kth topic.
+    * beta_t: Vx1 vector.  This is the underlying proportions.
+    * b2 scalar.
 
     """
 
@@ -133,7 +156,7 @@ def logitNormalSampler(z, theta_dit, alpha_it, a2, I):
                 un_u.append(random.uniform(exp(theta_kdit) / exp(sum(theta_dit)), 1))
         mx_mn = max(un_l)
         mn_mx = min(un_u)
-        theta_ditp.append(stats.truncnorm.ppf())
+        theta_ditp.append(stats.truncnorm.rvs(mx_mn, mn_mx, alpha_it[i], a2))
     return theta_ditp
 
 

### 2014-07-19 gamma_mcmc.py
z post code

@@ -109,12 +109,21 @@ def gammaPost(alpha_i, alpha_n, xi2, eta, delta2, I):
     return random.multivariate_normal(mu_gi, lambda_gi)
 
 
-def zPost(theta_itd, w, phi_tk):
+def zPost(theta_itd, w, phi_t):
     """
     
+    * theta_itd: Kx1 vector of proportions for topics
+    * w: Vx1 vector where the 1 value corresponds to the word
+    * phi_t: KxV matrix.  We iterate through the topics here and then take the correct
+    vocab for w.
+    
     """
-
-    return
+    
+    theta_phi = array([])
+    w_ind = where(w==1)[0][0]
+    for theta_itdk, phi_tk in zip(theta_itd, phi_t):
+        theta_phi.append((theta_itdk / sum(theta_itd)) * (phi_tk[w_ind] / sum(phi_tk)))
+    return random.multinomial(1, theta_phi)
 
 
 def logitNormalSampler(z, theta_dit, alpha_it, a2):

### 2014-07-19 gamma_mcmc.py
Update gamma_mcmc.py

@@ -192,6 +192,7 @@ def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2):
     beta_s = array([[[nan for v in range(V)] for t in range(T)] for s in range(S)])
     phi_s = array([[[[nan for v in range(V)] for k in range(K)] for t in range(T)] for s in range(S)])
     theta_s = array([[[[[nan for d in range(len(docs))] for docs in period] for period in node] for node in graph] for s in range(S)])
+    z_s = array([[[[[[nan for w in range(len(wrds))] for d in range(len(docs))] for docs in period] for period in node] for node in graph] for s in range(S)])
     
     # initialize start time
     t_1 = datetime.now()
@@ -228,7 +229,7 @@ def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2):
 
                         k = z[i, t, d, w]
                         z_s[s, i, t, d, w] = z[i, t, d, w]
-                        z[i, t, d, w] = zPost(theta[i, t, d], graph[i, t, d, w], phi[t, k])
+                        z[i, t, d, w] = zPost(theta[i, t, d], graph[i, t, d, w], phi[t])
 
 
         for t in range(1,T):
@@ -245,4 +246,4 @@ def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2):
 
         print datetime.now() - t_1, (s * 100.) / S
 
-    return gamma_s, alpha_s, beta_s, phi_s, theta_s
+    return gamma_s, alpha_s, beta_s, phi_s, theta_s, z_s

### 2014-07-19 gamma_mcmc.py
confused commit

@@ -192,7 +192,7 @@ def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2):
     beta_s = array([[[nan for v in range(V)] for t in range(T)] for s in range(S)])
     phi_s = array([[[[nan for v in range(V)] for k in range(K)] for t in range(T)] for s in range(S)])
     theta_s = array([[[[[nan for d in range(len(docs))] for docs in period] for period in node] for node in graph] for s in range(S)])
-    z_s = array([[[[[[nan for w in range(len(wrds))] for d in range(len(docs))] for docs in period] for period in node] for node in graph] for s in range(S)])
+    z_s = array([[[[[[nan for w in range(len(wrds))] for wrds in range(len(docs))] for docs in period] for period in node] for node in graph] for s in range(S)])
     
     # initialize start time
     t_1 = datetime.now()
@@ -227,7 +227,6 @@ def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2):
 
                     for w in range(w_it):
 
-                        k = z[i, t, d, w]
                         z_s[s, i, t, d, w] = z[i, t, d, w]
                         z[i, t, d, w] = zPost(theta[i, t, d], graph[i, t, d, w], phi[t])
 
@@ -246,4 +245,4 @@ def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2):
 
         print datetime.now() - t_1, (s * 100.) / S
 
-    return gamma_s, alpha_s, beta_s, phi_s, theta_s, z_s
+    return gamma_s, alpha_s, beta_s, phi_s, theta_s

### 2014-07-19 gamma_mcmc.py
update inputs fullRun

@@ -177,7 +177,7 @@ def genPrevAlpha(alpha, T, N):
     return alpha_n
 
 
-def fullRun(N, K, T, V, iterations, graph, vocab, xi2, delta2): 
+def fullRun(N, K, T, V, iterations, graph, vocab, xi2, sigma2, delta2, b2, a2): 
 
     # initalize values
     gamma = array([[1. / N for i in range(N)] for i in range(N)])

### 2014-07-19 test_mcmc.py
add full run test

@@ -61,3 +61,36 @@ a2 = 10.
 I = identity(10)
 
 theta_dit = gamma_mcmc.logitNormalSampler(z, theta_dit, theta_it, alpha_it, a2, I)
+
+# z post test
+
+theta_dit = 4 * random.rand(10) + 25
+phi_t = 4 * random.rand(10, 200) + 25
+w = zeros(200)
+w[random.randint(200)] = 1
+
+z_r = gamma_mcmc.zPost(theta_dit, w, phi_t)
+
+# full run test
+
+N = 20
+T = 15
+K = 10
+V = 200
+
+graph = array([])
+for i in range(N):
+    node = array([])
+    for t in range(T):
+        period = array([])
+        for d in range(random.randint(1, 10)):
+            doc = array([])
+            for w in range(random.randint(10, 300)):
+                wrd = zeros(200)
+                wrd[random.randint(200)] = 1
+                doc.append(wrd)
+            period.append(doc)
+        node.append(period)
+    graph.append(node)
+    
+res = gamma_mcmc.fullRun(N, T, K, V, graph, xi2, sigma2, delta2, b2, a2)

### 2014-07-20 paper/paper.tex
do gamma math
fix transpose
full run code
fix paper

@@
 
-\[= \frac{\theta_{it}^{I_{z_{jit}}=k}}{\sum_k \theta_{it}} \frac{\phi_{t}^{I_{w_{jit}}=v}}{\sum_v \phi_{kt}}\]
+\[= Mult\left(\left\{\frac{\theta_{kdit}}{\sum_{k'} \theta_{k'dit}}\frac{\phi_{kt}^{I_{w_{jit}}=v}}{\sum_v \phi_{kt}} \forall k \in K \right\}\right)\]
 
@@
 
+Let $\Xi(x) = x^Tx$
+
+\[p(\text{\boldmath$\alpha$}_i | \text{\boldmath$\alpha$}_{-1}, \gamma_i, \delta^2) = \prod_{t=2}^T p(\alpha_{it} | \alpha_{t-1}, \gamma_i, \delta^2)\]
+
+\[= \frac{1}{\sqrt{2 \pi \delta^2}} \exp\left(-\frac{1}{2\delta^2} \sum_{t=2}^T \Xi\left(\alpha_{it} - \alpha_{t-1}^T \gamma_i\right)\right)\]
+
 \[p(\gamma_i | \text{\boldmath$\alpha$}_{i}, \text{\boldmath$\alpha$}_{-1}, \eta, \xi^2) \propto p(\text{\boldmath$\alpha$}_i | \text{\boldmath$\alpha$}_{-1}, \gamma_i, \delta^2) p(\gamma_i | \eta, \xi^2)\]
 
-\[= N(\text{\boldmath$\alpha$}_{i};\text{\boldmath$\alpha$}_{-1}^T \gamma_i, \delta^2)N(\eta, \xi^2)\]
+\[\propto \exp\left(-\frac{1}{2 \delta^2} \sum_{t=2}^T \Xi\left(\alpha_{it} - \alpha_{t-1}^T \gamma_i\right)\right) \exp\left(-\frac{1}{2\xi^2}\Xi\left(\gamma_i - \eta\right)\right)\]
+
+\[= \exp\left(-\frac{1}{2 \delta^2} \sum_{t=2}^T \left(\Xi(\alpha_{it}) + \Xi\left(\alpha_{t-1}^T \gamma_i\right) - 2 \alpha_{it}^T (\alpha_{t-1}^T \gamma_i) \right)\right) \exp\left(-\frac{1}{2\xi^2}\left(\Xi(\gamma_i) + \Xi(\eta) - 2 \gamma_i^T \eta)\right)\right)\]
+
+\[= \exp\left(- \frac{\gamma_i^2}{2}\left(\frac{1}{\xi^2} + \frac{\Xi\left(\sum_{t=2}^T \alpha_{t-1}^T\right)}{\delta^2}\right) + \gamma_i \left(\frac{\eta}{\xi^2} + \frac{\left(\sum_{t=1}^T \alpha_{t-1}^T\right)^T \left(\sum_{t=2}^T \alpha_{it}\right)}{\delta^2}\right) - \left(\frac{\Xi(\eta)}{2\xi^2} + \frac{\Xi\left(\sum_{t=2}^T \alpha_{it}\right)}{2 \delta^2}\right)\right)\]
 
@@
 
-\[\Lambda_{\gamma i} = \left((\xi^2)^{-1} + \text{\boldmath$\alpha$}_{-1}^T(\delta^2)^{-1}\text{\boldmath$\alpha$}_{-1}\right)^{-1}\]
+\[\Lambda_{\gamma i} = \left(\frac{1}{\xi^2}+ \frac{\Xi\left(\sum_{t=2}^T \alpha_{t-1}^T\right)}{\delta^2}\right)^{-1}\]
 
-\[\mu_{\gamma i} = \Lambda_{\gamma i} \left((\xi^2)^{-1} \eta + \text{\boldmath$\alpha$}_{-1}^T(\delta^2)^{-1}\text{\boldmath$\alpha$}_{i}\right)\]
+\[\mu_{\gamma i} = \Lambda_{\gamma i} \left(\frac{\eta}{\xi^2} + \frac{\left(\sum_{t=1}^T \alpha_{t-1}^T\right)^T \left(\sum_{t=2}^T \alpha_{it}\right)}{\delta^2}\right)\]
 
@@
 
-Since this doesn't have a standard form we use a slice sampler to sample from the full conditional.
+Since this doesn't have a standard form I use the method suggested by Minmo et.
+al\footnote{Mimno, Wallach and McCallum.
+Gibbs Sampling for Logistic Normal Topic Models with Graph-Based Priors.
+2008.}.
 
@@
 
-\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(w_{jkt}; \pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, b^2)\]
+\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(w_{jkt}; \pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, \sigma^2)\]
 
-Since this doesn't have a standard form we use a slice sampler to sample from the full conditional.
+Since this doesn't have a standard form I use the method suggested by Minmo et. al.
 

### 2014-07-21 gamma_mcmc.py
update to fix run

@@ -1,5 +1,6 @@
 from numpy import *
 from datetime import datetime
+from scipy import stats
 
 def processWords(word):
     """returns vector of letters in vocab"""
@@ -119,10 +120,13 @@ def zPost(theta_itd, w, phi_t):
     
     """
     
-    theta_phi = array([])
+    l_theta_itd = len(theta_itd)
+    theta_phi = zeros(l_theta_itd)
     w_ind = where(w==1)[0][0]
+    i = 0
     for theta_itdk, phi_tk in zip(theta_itd, phi_t):
-        theta_phi.append((theta_itdk / sum(theta_itd)) * (phi_tk[w_ind] / sum(phi_tk)))
+        theta_phi[0] = (theta_itdk / sum(theta_itd)) * (phi_tk[w_ind] / sum(phi_tk))
+        i += 1
     return random.multinomial(1, theta_phi)
 
 
@@ -154,18 +158,21 @@ def logitNormalSampler(z, theta_dit, alpha_it, a2):
 
     """
 
-    theta_ditp = array([])
+    l_z = len(z)
+    l_theta_dit = len(theta_dit)
+    theta_ditp = zeros(l_theta_dit)
     for i, theta_kdit in enumerate(theta_dit):
-        un_l = array([])
-        un_u = array([])
-        for z_w in z:
+        un_l = array([nan for u in range(l_z)]) 
+        un_u = array([nan for u in range(l_z)])
+        for j, z_w in enumerate(z):
             if z_w[i] == 1:
-                un_l.append(random.uniform(0, exp(theta_kdit) / exp(sum(theta_dit))))
+                un_l[j] = random.uniform(0, exp(theta_kdit) / exp(sum(theta_dit)))
             else:
-                un_u.append(random.uniform(exp(theta_kdit) / exp(sum(theta_dit)), 1))
+                un_u[j] = random.uniform(exp(theta_kdit) / exp(sum(theta_dit)), 1)
         mx_mn = max(un_l)
         mn_mx = min(un_u)
-        theta_ditp.append(stats.truncnorm.rvs(mx_mn, mn_mx, alpha_it[i], a2))
+        theta_ditp[i] = stats.truncnorm.rvs(mx_mn, mn_mx, alpha_it[i], a2)
+    print theta_ditp
     return theta_ditp
 
 
@@ -177,7 +184,24 @@ def genPrevAlpha(alpha, T, N):
     return alpha_n
 
 
[…]

### 2014-07-21 test_mcmc.py

@@ -42,12 +42,11 @@ vocab = zeros((30, 200))
 for i, j in enumerate(random.randint(0, 200, size=(30))):
     vocab[i, j] = 1
 phi_kt = 4 * random.randn(200) + 25
-phi_t = 4 * random.randn(10, 200) + 25
 beta_t = random.randint(1, 20, size=(200))
 b2 = 10.
 I = identity(200)
 
-phi_kt = gamma_mcmc.logitNormalSampler(vocab, phi_kt, phi_t, beta_t, b2, I)
+phi_kt = gamma_mcmc.logitNormalSampler(vocab, phi_kt, beta_t, b2)
 
 # theta post test
 
@@ -55,12 +54,11 @@ z = zeros((30, 10))
 for i, j in enumerate(random.randint(0, 10, size=(30))):
     z[i, j] = 1
 theta_dit = 4 * random.randn(10) + 25
-theta_it = 4 * random.randn(5, 10) + 25
 alpha_it = random.randint(1, 20, size=(10))
 a2 = 10.
 I = identity(10)
 
-theta_dit = gamma_mcmc.logitNormalSampler(z, theta_dit, theta_it, alpha_it, a2, I)
+theta_dit = gamma_mcmc.logitNormalSampler(z, theta_dit, alpha_it, a2)
 
 # z post test
 
@@ -77,20 +75,18 @@ N = 20
 T = 15
 K = 10
 V = 200
+S = 500
 
-graph = array([])
+graph = array([[[[[0. for j in range(200)]
+                  for w in range(random.randint(10, 300))]
+                 for d in range(random.randint(1, 10))]
+                for t in range(T)]
+               for i in range(N)])
+
 for i in range(N):
-    node = array([])
     for t in range(T):
-        period = array([])
-        for d in range(random.randint(1, 10)):
-            doc = array([])
-            for w in range(random.randint(10, 300)):
-                wrd = zeros(200)
-                wrd[random.randint(200)] = 1
-                doc.append(wrd)
-            period.append(doc)
-        node.append(period)
-    graph.append(node)
+        for d in range(len(graph[i][t])):
+            for w in range(len(graph[i][t][d])):
+                graph[i][t][d][w][random.randint(200)] = 1
     
-res = gamma_mcmc.fullRun(N, T, K, V, graph, xi2, sigma2, delta2, b2, a2)
+res = gamma_mcmc.fullRun(N, T, K, V, S, graph, xi2, sigma2, delta2, b2, a2)

### 2014-07-22 build_data_dict.py
clean data

@@ -1,0 +1,69 @@
+from datetime import datetime
+import cPickle
+import csv
+import sys
+import os
+
+
+def buildVocab(csv_f):
+    """builds the vocab for the data"""
+    
+    t_1 = datetime.now()
+
+    vocab = []
+    reader = csv.reader(open(csv_f), "rb"))
+    reader_l = list(reader)
+    ln = len(reader_l)
+    for i, row in enumerate(reader_l):
+        text = row[2]
+        text_l = text.split(" ")
+        for word in text_l:
+            if word not in vocab:
+                vocab.append(word)
+        print (i * 100.) / ln, datetime.now() - t_1, i
+    return vocab
+
+
+def buildData(csv_f, vocab):
+    """builds the dataset"""
+
+    t_1 = datetime.now()
+
+    data = {}
+    reader = csv.reader(open(csv_f), "rb"))
+    reader_l = list(reader)
+    ln = len(reader_l)
+    for i, row in enumerate(reader_l):
+        text = row[2].split(" ")
+        node = row[1]
+        dateb = row[0].split(" ")
+        period = dateb[1] + " " + dateb[2] + " " + dateb[5]
+        if node in data:
+            if period in data[node]:
+                doc = []
+                for w in text:
+                    doc.append(vocab.index(w))
+                data[node][period].append(doc)
+            else:
+                data[node][period] = []
+                doc = []
+                for w in text:
+                    doc.append(vocab.index(w))
+                data[node][period].append(doc)
+        else:
+            data[node] = {}
+            data[node][period] = []
+            doc = []
+            for w in text:
+                doc.append(vocab.index(w))
+            data[node][period].append(doc)
+        print (i * 100.) / ln, datetime.now() - t_1, i
+    return data
+
+
+os.chdir(sys.argv[3])
+csv_f = sys.argv[1]
+
+vocab = buildVocab(csv_f)
+data = buildData(csv_f, vocab)
+cPickle.dump(data, open(sys.argv[2], "wb"))

### 2014-07-22 data_extractor.py

@@ -1,0 +1,27 @@
+from datetime import datetime
+from pymongo import MongoClient
+import sys
+import csv
+import os
+
+
+client = MongoClient()
+db = client["StreamingDb"]
+collection = db["StreamingCollection"]
+
+# prep for search
+ln = collection.count()
+t_1 = datetime.now()
+i = 0
+
+os.chdir(sys.argv[2])
+for obs in collection.find():
+    f_name = open(sys.argv[1], "ab")
+    writer = csv.writer(f_name)
+    text = obs["text"].encode("utf-8")
+    agent = obs["user"]["screen_name"]
+    date = obs["created_at"]
+    writer.writerow([date, agent, text])
+    f_name.close()
+    print (i * 100.) / ln, datetime.now() - t_1, i
+    i += 1

### 2014-07-22 test_mcmc.py

@@ -41,13 +41,12 @@ gamma_r = gamma_mcmc.gammaPost(alpha_i, alpha_n, xi2, eta, delta2, I)
 vocab = zeros((30, 200))
 for i, j in enumerate(random.randint(0, 200, size=(30))):
     vocab[i, j] = 1
-phi_kt = 4 * random.randn(200) + 25
 phi_t = 4 * random.randn(10, 200) + 25
 beta_t = random.randint(1, 20, size=(200))
 b2 = 10.
 I = identity(200)
 
-phi_kt = gamma_mcmc.logitNormalSampler(vocab, phi_kt, phi_t, beta_t, b2, I)
+phi_kt = gamma_mcmc.logitNormalSampler(vocab, phi_t, beta_t, b2)
 
 # theta post test
 
@@ -55,12 +54,11 @@ z = zeros((30, 10))
 for i, j in enumerate(random.randint(0, 10, size=(30))):
     z[i, j] = 1
 theta_dit = 4 * random.randn(10) + 25
-theta_it = 4 * random.randn(5, 10) + 25
 alpha_it = random.randint(1, 20, size=(10))
 a2 = 10.
 I = identity(10)
 
-theta_dit = gamma_mcmc.logitNormalSampler(z, theta_dit, theta_it, alpha_it, a2, I)
+theta_dit = gamma_mcmc.logitNormalSampler(z, theta_dit, alpha_it, a2)
 
 # z post test
 

### 2014-07-22 gamma_mcmc.py
update to match

@@ -1,0 +1,280 @@
+from numpy import *
+from datetime import datetime
+from scipy import stats
+
+def processWords(word):
+    """returns vector of letters in vocab"""
+
+    return
+
+
+def alphaPost(alpha_n1, gamma_i, delta2, a2, theta_it, I, d_it):
+    """generates the full conditional for alpha_it
+    
+    * delta2: scalar
+    * a2: scalar
+    * I: KxK identity matrix
+    * d_it: scalar, the number of documents for a given node in a given
+    period
+    * alpha_n1: NxK matrix of proportions for each node.  Each row is a
+    node and each column is a proportion
+    * gamma_i: Nx1 vector, each element is a weight for that node
+    * theta_it: DxK matrix of draws for each document.  Each row is the
+    document and each column is the topic
+    * mu_ait: Kx1 vector
+
+    NOTES:
+
+    * theta_it.sum(axis=0) sums all the columns so you get a Kx1 vector
+    that is the sum of thetas over the documents
+    * dot(alpha_n1, gamma_i) is a Kx1 vector for the "mean".
+    * 1 / delta2 * I is a KxK diagonal matrix with 1 / delta2 in the diagonal
+    * d_it / a2 * I is a KxK diagonal matrix with d_it / a2 in the diagonal
+    * dot(transpose(1 / delta2 * I), dot(transpose(alpha_n1), gamma_i)) is
+    a Kx1 vector for the prior
+    * dot(transpose(d_it / a2 * I), theta_it.sum(axis=0)) is a Kx1 vector
+    for the data
+
+    * lambda_ait is a KxK matrix of the covariance
+    * mu_ait is a Kx1 vector for the mean
+
+    """
+
+    lambda_ait = linalg.inv(1 / delta2 * I + d_it / a2 * I)
+    mu_ait = dot(transpose(lambda_ait), (dot(transpose(1 / delta2 * I),
+                                             dot(transpose(alpha_n1), gamma_i))
+                                         + dot(transpose(d_it / a2 * I),
+                                               theta_it.sum(axis=0))))
+    return random.multivariate_normal(mu_ait, lambda_ait)
+
+
+def betaPost(beta_n1, sigma2, b2, phi_t, I, k):
+    """generates the full conditional for beta_t
+
+    * sigma2: scalar
+    * b2: scalar
+    * I: VxV identity matrix
+    * k: scalar, the number of topics
+    * beta_n1: Vx1 vector
[…]

### 2014-07-22 test_mcmc.py

@@ -1,0 +1,92 @@
+import gamma_mcmc
+from numpy import *
+
+# alphaPost test
+
+alpha_n1 = random.randint(1, 20, size=(20, 10))
+gamma_i = random.rand(20)
+delta2 = 10.
+a2 = 10.
+theta_it = 4 * random.randn(5, 10) + 25
+I = identity(10)
+d_it = 5
+
+alpha_r = gamma_mcmc.alphaPost(alpha_n1, gamma_i, delta2, a2, theta_it, I, d_it)
+
+# betaPost test
+
+beta_n1 = random.randint(1, 20, size=200)
+sigma2 = 10.
+b2 = 10.
+phi_t = 4 * random.randn(10, 200) + 25
+I = identity(200)
+k = 10
+
+beta_r = gamma_mcmc.betaPost(beta_n1, sigma2, b2, phi_t, I, k)
+
+# gammaPost test
+
+alpha_i = random.randint(1, 20, size=(15, 10))
+alpha_n = random.randint(1, 20, size=(15, 20, 10))
+xi2 = 10.
+eta = random.rand(20)
+delta2 = 10.
+I = identity(20)
+
+gamma_r = gamma_mcmc.gammaPost(alpha_i, alpha_n, xi2, eta, delta2, I)
+
+
+# phi post test
+
+vocab = zeros((30, 200))
+for i, j in enumerate(random.randint(0, 200, size=(30))):
+    vocab[i, j] = 1
+phi_kt = 4 * random.randn(200) + 25
+beta_t = random.randint(1, 20, size=(200))
+b2 = 10.
+I = identity(200)
+
+phi_kt = gamma_mcmc.logitNormalSampler(vocab, phi_kt, beta_t, b2)
+
+# theta post test
+
+z = zeros((30, 10))
+for i, j in enumerate(random.randint(0, 10, size=(30))):
+    z[i, j] = 1
+theta_dit = 4 * random.randn(10) + 25
+alpha_it = random.randint(1, 20, size=(10))
+a2 = 10.
+I = identity(10)
+
+theta_dit = gamma_mcmc.logitNormalSampler(z, theta_dit, alpha_it, a2)
+
+# z post test
+
+theta_dit = 4 * random.rand(10) + 25
+phi_t = 4 * random.rand(10, 200) + 25
+w = zeros(200)
+w[random.randint(200)] = 1
+
+z_r = gamma_mcmc.zPost(theta_dit, w, phi_t)
+
[…]

### 2014-07-22 build_data_dict.py
any other changes

@@ -11,7 +11,7 @@ def buildVocab(csv_f):
     t_1 = datetime.now()
 
     vocab = []
-    reader = csv.reader(open(csv_f), "rb"))
+    reader = csv.reader(open(csv_f, "rb"))
     reader_l = list(reader)
     ln = len(reader_l)
     for i, row in enumerate(reader_l):
@@ -30,7 +30,7 @@ def buildData(csv_f, vocab):
     t_1 = datetime.now()
 
     data = {}
-    reader = csv.reader(open(csv_f), "rb"))
+    reader = csv.reader(open(csv_f, "rb"))
     reader_l = list(reader)
     ln = len(reader_l)
     for i, row in enumerate(reader_l):

### 2014-07-23 text_cleaner.py
new data cleaner

@@ -1,0 +1,80 @@
+from datetime import datetime
+from nltk.tokenize import word_tokenize
+from nltk.corpus import stopwords
+from nltk import PorterStemmer
+import re
+import csv
+
+
+def addWordTDict(w, date, node, data_dict):
+    """"""
+
+    if date in data_dict:
+        if node in data_dict[date]:
+            if w in data_dict[date][node]:
+                data_dict[date][node][w] += 1
+            else:
+                data_dict[date][node][w] = 1
+        else:
+            data_dict[date][node] = {}
+            data_dict[date][node][w] = 1
+    else:
+        data_dict[date] = {}
+        data_dict[date][node] = {}
+        data_dict[date][node][w] = 1
+    return data_dict
+
+
+def extractData(csv_f):
+    """extracts the data from the csv"""
+
+    rx = re.compile("\W+")
+
+    t_1 = datetime.now()
+    data_dict = {}
+
+    reader = csv.reader(open(csv_f, "rb"))
+    reader_l = list(reader)
+    reader_ln = len(reader_l)
+    for i, row in enumerate(reader_l):
+        text = row[2]
+        node = row[1]
+        dateb = row[0].split(" ")
+        period = dateb[1] + " " + dateb[2] + " " + dateb[5]
+        text = text.lower()
+        text = rx.sub(" ", t).strip()
+        for w in word_tokenize(text):
+            w = PorterStemmer.stem_word(w)
+            if w not in stopwords.words("english"):
+                data_dict = addWordTDict(w, period, node, data_dict)
+        print (i * 100.) / data_ln, datetime.now() - t_1
+
+
+def getVocab(data_dict):
+    """gets the vocab from a data_dict"""
+
+    t_1 = datetime.now()
+    vocab = []
+    data_ln = len(data_dict)
+    for i, d in enumerate(data_dict):
+        for n in data_dict[d]:
+            wrds = data_dict[d][n].keys()
+            for w in wrds:
+                if w not in vocab:
+                    vocab.append(w)
+        print (i * 100.) / data_ln, datetime.now() - t_1, "vocab"
+    return vocab
+
+
+def writeDictionary(data_dict, csv_f, vocab):
+    """writes the dictionary to a csv file"""
+
+    t_1 = datetime.now()
+    data_ln = len(data_dict)
+    writer = csv.writer(open(csv_f, "wb"))
+    for i, d in enumerate(data_dict):
+        for n in data_dict[d]:
[…]

### 2014-07-23 paper/paper.tex
full conditionals alt model
fix paper and fix text cleaner

@@
 
-\[p(a^2 | \nu_0, \tau_0) = IW(\nu_0, \tau_0)\]
-
-\[p(b^2 | \nu_1, \tau_1) = IW(\nu_1, \tau_1)\]
-
 \[p(z| \theta) = Mult(\pi(\theta))\]
@@
 
-\subsection{Posterior Specification for $b^2$}
-
-\[p(b^2|\beta,\phi) \propto \prod_{t=1}^T \prod_{k=1}^K p(\phi_{kt} | \beta_t, b^2)p(b^2 | \nu_0, \tau_0) \]
-
-\[= \prod_{t=1}^T \prod_{k=1}^K N(\phi_{kt};\beta_t, b^2)IW(\nu_0, \tau_0)\]
-
-\[\propto IW\left(\nu_0 + TK, \left(\tau_0 + \sum_{t=1}^T \sum_{k=1}^K (\phi_{kt} - \beta_t)(\phi_{kt} - \beta_t)^T\right)^{-1}\right)\]
-
 \subsection{Posterior Specification for $\alpha_{it}$}
@@
 \[\mu_{\alpha i t} = \Lambda_{\alpha i t} \left((\delta^2)^{-1}\text{\boldmath$\alpha$}_{t-1} \gamma_i + d_i (a^2)^{-1} \sum_{d=1}^{D_i} \theta_{dit}\right) \]
-
-\subsection{Posterior Specification for $a^2$}
-
-\[p(a^2|\alpha,\theta) \propto \prod_{t=1}^T \prod_{i=1}^N \prod_{d=1}^{D_i} p(\theta_{dit} | \alpha_{it}, a^2)p(a^2 | \nu_1, \tau_1) \]
-
-\[= \prod_{t=1}^T \prod_{i=1}^N \prod_{k=1}^K N(\theta_{dit};\alpha_{it}, a^2)IW(\nu_1, \tau_1)\]
-
-This needs to be fixed
-
-\[\propto IW\left(\nu_1 + TND, \left(\tau_0 + \sum_{t=1}^T \sum_{i=1}^N \sum_{d=1}^{D_i} (\theta_{dit} - \alpha_{it})(\theta_{dit} - \alpha_{dit})^T\right)^{-1}\right)\]
 
@@
 
+\section{Full Conditionals for the Alternative Model}
+
+\[p(\gamma_i | \eta, \xi^2) = N(\eta, \xi^2)\]
+
+\[p(\alpha_i|\chi,\sigma^2) = N(\chi, \sigma^2)\]
+
+\[\text{\boldmath$\alpha$} = \{\alpha_1, \alpha_2, ...,\alpha_N\}\]
+
+\[p(\theta_{it}| \alpha_i, \gamma_i,\delta^2) = N(\text{\boldmath$\alpha$}^T \gamma_i, \delta^2)\]
+
+\[p(\phi_k | \beta) = Dir(\beta)\]
+
+\[p(z_{itj}| \theta_{it}) = Mult(\pi(\theta_{it}))\]
+
+\[p(w_{itj} | \phi, z_{itj}) = Mult(\phi_{z_{itj}})\]
+
+\[p(\theta, \phi, \gamma, \alpha, \beta, z | w) \propto \prod_{i=1}^N \prod_{t=1}^T \prod_{j=1}^{J_{ti}} \prod_{k=1}^K p(w_{itj} | \phi, z_{itj}) p(z_{itj} | \theta_{it}) p(\phi_k | \beta) p(\theta_{it} | \alpha_i, \gamma_i, \delta^2) p(\alpha_i | \chi, \sigma^2) p(\gamma_i | \eta, xi^2)\]
+
 \end{document}

### 2014-07-23 text_cleaner.py

@@ -25,7 +25,7 @@ def addWordTDict(w, date, node, data_dict):
     return data_dict
 
 
-def extractData(csv_f):
+def extractData(csv_f, month_date):
     """extracts the data from the csv"""
 
     rx = re.compile("\W+")
@@ -40,14 +40,18 @@ def extractData(csv_f):
         text = row[2]
         node = row[1]
         dateb = row[0].split(" ")
-        period = dateb[1] + " " + dateb[2] + " " + dateb[5]
+        if month_date:
+            period = dateb[2] + " " + dateb[5]
+        else:
+            period = dateb[1] + " " + dateb[2] + " " + dateb[5]
         text = text.lower()
-        text = rx.sub(" ", t).strip()
+        text = rx.sub(" ", text).strip()
         for w in word_tokenize(text):
-            w = PorterStemmer.stem_word(w)
+            w = PorterStemmer().stem_word(w)
             if w not in stopwords.words("english"):
                 data_dict = addWordTDict(w, period, node, data_dict)
-        print (i * 100.) / data_ln, datetime.now() - t_1
+        print (i * 100.) / reader_ln, datetime.now() - t_1
+    return data_dict
 
 
 def getVocab(data_dict):
@@ -78,3 +82,11 @@ def writeDictionary(data_dict, csv_f, vocab):
                 if v in data_dict[d][n]:
                     writer.writerow([v, d, n, data_dict[d][n][v]])
         print (i * 100.) / data_ln, datetime.now() - t_1, "csv"
+
+
+def fullRun(i_csv_f, o_csv_f, month_date=False):
+    """does a full run"""
+
+    data_dict = extractData(i_csv_f, month_date)
+    vocab = getVocab(data_dict)
+    writeDictionary(data_dict, o_csv_f, vocab)

### 2014-07-24 paper/paper.tex
appendix b

@@
 
-\section{Full Conditionals}
+\section{Full Conditionals\\ NOTE: This section is now out of date, see Appendix B}
 
@@
 
-\[p(\theta, \phi, \gamma, \alpha, \beta, z | w) \propto \prod_{i=1}^N \prod_{t=1}^T \prod_{j=1}^{J_{ti}} \prod_{k=1}^K p(w_{itj} | \phi, z_{itj}) p(z_{itj} | \theta_{it}) p(\phi_k | \beta) p(\theta_{it} | \alpha_i, \gamma_i, \delta^2) p(\alpha_i | \chi, \sigma^2) p(\gamma_i | \eta, xi^2)\]
+\[p(\theta, \phi, \gamma, \alpha, \beta, z | w) \propto \prod_{i=1}^N \prod_{t=1}^T \prod_{j=1}^{J_{it}} p(w_{itj} | \phi, z_{itj}) p(z_{itj} | \theta_{it}) p(\phi_k | \beta) p(\theta_{it} | \alpha_i, \gamma_i, \delta^2) p(\alpha_i | \chi, \sigma^2) p(\gamma_i | \eta, xi^2)\]
+
+\subsection{Posterior Specification for $\gamma_i$}
+
+\[p(\gamma_i | \text{\boldmath$\alpha$}, \delta^2, \theta_i, \eta, \xi^2) \propto p(\theta_i | \text{\boldmath$\alpha$}, \gamma_i, \delta^2)p(\eta, \xi^2)\]
+
+\[\prod_{t=1}^T N(\text{\boldmath$\alpha$}^T \gamma_i, \delta^2) N(\eta, \xi^2)\]
+
+\[\]
+
+\subsection{Posterior Specification for $\theta_{it}$}
+
+\[p(\theta_{it} | z, \text{\boldmath$\alpha$}, \gamma_i, \delta^2) \propto p(z_{it}| \theta_{it}) p(\theta_{it} | \text{\boldmath$\alpha$}, \gamma_i, \delta^2)\]
+
+\[= \prod_{j=1}^{J_{it}} Mult(\pi(\theta_{it})) N(\text{\boldmath$\alpha$}^T\gamma_i, \delta^2)\]
+
+Since this doesn't have a standard form I use the method suggested by Minmo et.
+al\footnote{Mimno, Wallach and McCallum.
+Gibbs Sampling for Logistic Normal Topic Models with Graph-Based Priors.
+2008.}.
+
+\subsection{Posterior Specification for $\phi_k$}
+
+\[p(\phi_k | \beta, z, w) \propto p(w | \phi_k, z) p(\phi_k | \beta)\]
+
+\[= \prod_{j=1}^{J_{z=k}} Mult(\phi_k) Dir(\beta)\]
+
+\[\propto Dir\left(\beta + \sum_{j=1}^{J_{z=k}}w_j \right)\]
+
+$w_j$ is this case is a $v$ vector with a one for the $w$th element and 0 everywhere else.
+
+\subsection{Posterior Specification for $z_{itj}$}
+
+\[p(z_{itj} | w_{itj}, \theta_{it}, \phi) \propto p(w_{itj} | \phi, z_{itj}) p(z_{itj} | \theta_{it})\]
+
+\[= Mult\left(\left\{\frac{\theta_{kit}}{\sum_{k'} \theta_{k'it}}\frac{\phi_{k}^{I_{w_{itj}}=v}}{\sum_v \phi_{vk}} \forall k \in K \right\}\right)\]
 

### 2014-07-25 text_cleaner.py
clean extract data

@@ -70,7 +70,7 @@ def getVocab(data_dict):
     return vocab
 
 
-def writeDictionary(data_dict, csv_f, vocab):
+def writeDictionary(data_dict, csv_f):
     """writes the dictionary to a csv file"""
 
     t_1 = datetime.now()
@@ -78,9 +78,8 @@ def writeDictionary(data_dict, csv_f, vocab):
     writer = csv.writer(open(csv_f, "wb"))
     for i, d in enumerate(data_dict):
         for n in data_dict[d]:
-            for v in vocab:
-                if v in data_dict[d][n]:
-                    writer.writerow([v, d, n, data_dict[d][n][v]])
+            for w in data_dict[d][n][w]:
+                writer.writerow([w, d, n, data_dict[d][n][w]])
         print (i * 100.) / data_ln, datetime.now() - t_1, "csv"
 
 
@@ -88,5 +87,4 @@ def fullRun(i_csv_f, o_csv_f, month_date=False):
     """does a full run"""
 
     data_dict = extractData(i_csv_f, month_date)
-    vocab = getVocab(data_dict)
-    writeDictionary(data_dict, o_csv_f, vocab)
+    writeDictionary(data_dict, o_csv_f)

### 2014-07-25 get_user_id.py
user info scraper

@@ -1,0 +1,55 @@
+import tweepy
+import cPickle
+import sys
+import os
+import time
+import ConfigParser
+from datetime import datetime
+
+
+def authorize(consumer_key, consumer_secret,
+              access_token, access_token_secret):
+    """authorize the Twitter API"""
+
+    auth = tweepy.OAuthHandler(consumer_key, consumer_secret)
+    auth.set_access_token(access_token, access_token_secret)
+    api = tweepy.API(auth)
+    return api
+
+
+os.chdir(sys.argv[1])
+Config = ConfigParser.ConfigParser()
+Config.read("twitter.config")
+consumer_key = Config.get("Twitter", "consumer_key")
+consumer_secret = Config.get("Twitter", "consumer_secret")
+access_token = Config.get("Twitter", "access_token")
+access_token_secret = Config.get("Twitter", "access_token_secret")
+api = authorize(consumer_key, consumer_secret,
+                access_token, access_token_secret)
+
+twitter_dict = cPickle.load(open("twitter_links.pkl"))
+twitter_links = [twitter_dict[k][0].split("/")[-1] for k in twitter_dict.keys()]
+
+timelines = {}
+user_ids = []
+t_1 = datetime.now()
+for i, link in enumerate(twitter_links):
+    try:
+        timeline = api.user_timeline(link)
+        timelines[link] = timeline
+        print timeline[0].user.id, i, datetime.now() - t_1
+        user_ids.append(timeline[0].user.id)
+        time.sleep(5)
+    except:
+        try:
+            time.sleep(30)
+            timeline = api.user_timeline(link)
+            timeline[link] = timeline
+            print timeline[0].user.id, i, datetime.now() - t_1
+            user_ids.append(timeline[0].user.id)
+            time.sleep(5)
+        except:
+            print "Error", link, i
+
+cPickle.dump(user_ids, open("user_ids.pkl", "wb"))
+cPickle.dump(timelines, open("timelines.pkl", "wb"))

### 2014-07-25 mongodb_scraper.py

@@ -66,8 +66,8 @@ api = authorize(consumer_key, consumer_secret,
 #load user list
 
 twitter_dict = cPickle.load(open("twitter_links.pkl"))
-twitter_links = [twitter_dict[k][-1] for k in twitter_dict.keys()]
-twitter_links = [str(t) for t in twitter_links if type(t) == int]
+twitter_links = [twitter_dict[k][0].split("/")[-1] for k in twitter_dict.keys()]
+print twitter_links
 # This is a very hacky solution to a problem that I keep running into, the streaming scraper keeps crashing with an IncompleteRead error, I am going to have to rewrite a lot of this at a lower level at somepoint but this makes the scraper work for now.
 t_1 = datetime.now()
 while True:

### 2014-07-25 streaming_scraper.py

@@ -59,7 +59,7 @@ api = authorize(consumer_key, consumer_secret,
 #load user list
 
 twitter_dict = cPickle.load(open("twitter_links.pkl"))
-twitter_links = [twitter_dict[k][-1] for k in twitter_dict]
+twitter_links = [twitter_dict[k][0].split("/")[-1] for k in twitter_dict]
 # This is a very hacky solution to a problem that I keep running into, the streaming scraper keeps crashing with an IncompleteRead error, I am going to have to rewrite a lot of this at a lower level at somepoint but this makes the scraper work for now.
 t_1 = datetime.now()
 while True:

### 2014-07-25 text_cleaner.py

@@ -78,7 +78,7 @@ def writeDictionary(data_dict, csv_f):
     writer = csv.writer(open(csv_f, "wb"))
     for i, d in enumerate(data_dict):
         for n in data_dict[d]:
-            for w in data_dict[d][n][w]:
+            for w in data_dict[d][n]:
                 writer.writerow([w, d, n, data_dict[d][n][w]])
         print (i * 100.) / data_ln, datetime.now() - t_1, "csv"
 

### 2014-07-25 paper/paper.tex
add posterior for gamma
fix posterior
truth

@@
 
+\subsection{Supra-Bayesian Truth Estimation}
+
+Imagine that you are a decision maker observing the network of media firms.
+You wish to develop some estimate of "truth" for each news story you observe based on who is posting about the news story.
+To do this you may approach the problem as a supra-Bayesian.
+Consider that each agent in the network has some belief about the truth of a news event $p_i(T | \textbf{s})$ where $\textbf{s}$ is some signal about the world.
+The supra-Bayesian would treat each agent's beliefs as data for his own beliefs
+
+\[p(T | \bar{p}) \propto p(\bar{p} | T) p(T)\]
+
+where $\bar{p} = \{p_1(T | \textbf{s}), ... p_N(T | \textbf{s})\}$.  If each agent's beliefs and signals were indepedent then this would be the same as
+
+\[p(T | \bar{p}) \propto p(p_1 | T), .... p(p_N | T) p(T)\]
+
+However, this is obviously not the case here as each agent can observe the signals of other agents and decide what to publish based on this.
+So we need some way to control for the possible noise from other signals.
+Ultimately, we want the probability of each agent holding their beliefs, given only their own signals.
+If we have this then we can follow the above indepedent framework.
+
+Let $p(p_i | T, \{s_j \forall j \in J\})$ be the probability of the $i$th agent holding their beliefs given a set of signals from the set of $J$ agents.
+In this case $p(p_i | T, s_i)$ would be the probability of the $i$th agent holding their beliefs in the case where they receive no other signals.
+This could also be written as $p(p_i | T, \!\{s_j \forall j \in J_{-i}\})$.
+In the general case we can see that
+
+\[p(p_i | T, \{s_j \forall j \in J\}) = \prod_{j=1}^J \gamma_{ij} p(p_i | T)\]
+
+because $\gamma_{ij}$ is the trust that agent $i$ holds for $j$ and represents the probability that $i$ will use a signal from $j$.  Then we can see that
+
+\[p(p_i | T, s_i) = p(p_i | T, \!\{s_j \forall j \in J_{-i}\}) = \prod_{j=1}^{J_{-i}} (1 - \gamma_{ij}) p(p_i | T)\]
+
+Now consider the two agent case with the supra-Bayesian
+
+\[p(T | \bar{p}) \propto (1 - \gamma_{12}) p(p_1 | T) (1 - \gamma_{21}) p(p_2 | T)  p(T)\]
+
+This then provides a clear way to estimate the "truth" of a news story based on the dispersed beliefs of agents in a network.  NOTE: more on how to actually implement.
+
 \subsection{Estimating Bias-Free Quality}
@@
 The intuition behind this measure is that higher quality firms should be more trusted by all firms controlling for bias.
+
+\subsection{Supra-Bayesian Quality Estimation}
 
@@
 \section{Implementation}
+
+NOTE: This section needs to be updated, the model is now completely different.
 
@@
 
+\subsection{Posterior Specification for $\alpha_i$}
+
+\[p(\alpha_i | \text{\boldmath$\alpha$}_{-i}, \gamma_i, \delta^2, \sigma^2, \chi) \propto p(\theta_i | \text{\boldmath$\alpha$}, \gamma_i, \delta^2) p(\alpha_i | \chi, \sigma^2)\]
+
+\[= \prod_{t=1}^T N(\text{\boldmath$\alpha$}^T \gamma_i, \delta^2) N(\chi, \sigma^2)\]
+
+\[\propto \exp\left\{-\frac{1}{2}\frac{(\text{\boldmath$\alpha$}^T \gamma_i)^T (\text{\boldmath$\alpha$}^T \gamma_i)}{\delta^2} + \frac{\sum_{t=1}^T (\text{\boldmath$\alpha$}^T \gamma_i)^T \theta_{it}}{\delta^2}\right\} \exp\left\{-\frac{1}{2}\frac{\alpha_i^T \alpha_i}{\sigma^2} + \frac{\alpha_i^T \chi}{\sigma^2}\right\}\]
+
+\[\propto  \exp\left\{-\frac{1}{2}\frac{(\alpha_i \gamma_{ii})^T (\alpha_i^T \gamma_{ii})}{\delta^2} + \frac{\sum_{t=1}^T (\alpha_i^T \gamma_{ii})^T \theta_{it}}{\delta^2}\right\} \exp\left\{-\frac{1}{2}\frac{\alpha_i^T \alpha_i}{\sigma^2} + \frac{\alpha_i^T \chi}{\sigma^2}\right\}\]
+
+\[\propto N(\mu_{\alpha i}, \Lambda_{\alpha i})\]
+
+\[\Lambda_{\alpha i} = \left(\frac{I}{\sigma^2} + \frac{\gamma_{ii}^2}{\delta^2}\right)^{-1}\]
+
+\[\mu_{\alpha i} = \Lambda_{\alpha i} \left(\frac{\chi}{\sigma^2} + \frac{T \gamma_{ii} \sum_{t=1}^T \theta_{it}}{\delta^2}\right)\]
+
 \subsection{Posterior Specification for $\gamma_i$}
@@
 
-\[\prod_{t=1}^T N(\text{\boldmath$\alpha$}^T \gamma_i, \delta^2) N(\eta, \xi^2)\]
+\[= \prod_{t=1}^T N(\text{\boldmath$\alpha$}^T \gamma_i, \delta^2) N(\eta, \xi^2)\]
 
-\[\]
+\[\propto N(\mu_{\gamma i}, \Lambda_{\gamma i})\]
+
+\[\Lambda_{\gamma i} = \left(\frac{I}{\xi^2} + \frac{\text{\boldmath$\alpha$}\text{\boldmath$\alpha$}^T}{\delta^2}\right)^{-1}\]
+
+\[\mu_{\gamma i} = \Lambda_{\gamma i} \left(\frac{\eta}{\xi^2} + \frac{T\text{\boldmath$\alpha$} \sum_{t=1}^T \theta_{it}}{\delta^2}\right)\]
 

### 2014-07-25 paper/paper.tex
quality

@@
 
+Consider that you want to estimate a measure of "quality" from the agent's beliefs about the quality of another agent following the supra-Bayesian approach mentioned above.
+Following the approach taken above
+
+\[p(Q | \bar{p}) \propto p(\bar{p} | Q) p(Q)\]
+
+In this case consider that each agent's belief about the quality of another agent is independent from the other agents beliefs about the quality of the agent.  Then
+
+\[p(Q | \bar{p}) \propto p(p_1 | Q), .... p(p_N | Q) p(Q)\]
+
+However, we know that there are number of characterisitc that could effect an agents belief about the quality of another agent.
+Consider that there are G biases that influence an agents belief about another agents quality.
+The overall measure of quality can then be determined by
+
+\[p(p_i | Q) \propto p(p_i | Q_1) + ... + p(p_i | Q_G)\]
+
+Let $p(p_i | Q_1)$ be the bias free measure of quality.
+Then we can get the bias free measure of quality by subtracting each biased measure from the observed measure of quality.
+Then if we want to estimate the bias-free measure of quality this can be taken from
+
+\[p(Q_1 | \bar{p}) \propto (p(p_1 | Q) - \sum_{j=2}^G p(p_1 | Q_j)) ... (p(p_N | Q) - \sum_{j=2}^G p(p_N | Q_j)) p(Q_1)\]
+
 \subsection{The Significance of Border Cases}

### 2014-07-26 mongodb_scraper.py
small updates

@@ -65,9 +65,8 @@ api = authorize(consumer_key, consumer_secret,
 
 #load user list
 
-twitter_dict = cPickle.load(open("twitter_links.pkl"))
-twitter_links = [twitter_dict[k][0].split("/")[-1] for k in twitter_dict.keys()]
-print twitter_links
+twitter_links = cPickle.load(open("user_ids.pkl"))
+twitter_links = [str(i) for i in twitter_links]
 # This is a very hacky solution to a problem that I keep running into, the streaming scraper keeps crashing with an IncompleteRead error, I am going to have to rewrite a lot of this at a lower level at somepoint but this makes the scraper work for now.
 t_1 = datetime.now()
 while True:

### 2014-07-27 data_extractor_rest.py
new cleaner

@@ -1,0 +1,39 @@
+from datetime import datetime
+from pymongo import MongoClient
+import cPickle
+import sys
+import csv
+import os
+
+
+client = MongoClient()
+db = client["StreamingDb"]
+collection = db["StreamingCollection"]
+
+# prep for search
+ln = collection.count()
+t_1 = datetime.now()
+i = 0
+
+os.chdir(sys.argv[2])
+for obs in collection.find():
+    f_name = open(sys.argv[1], "ab")
+    writer = csv.writer(f_name)
+    text = obs["text"].encode("utf-8")
+    agent = obs["user"]["screen_name"]
+    date = obs["created_at"]
+    writer.writerow([date, agent, text])
+    f_name.close()
+    print (i * 100.) / ln, datetime.now() - t_1, i, "db"
+    i += 1
+
+rest_timelines = cPickle.load(open(sys.argv[3], "rb"))
+for link in rest_timelines:
+    for tweet in rest_timelines[link]:
+        f_name = open(sys.argv[1], "ab")
+        writer = csv.writer(f_name)
+        text = tweet.text.encode("utf-8")
+        agent = tweet.user.screen_name
+        date = tweet.created_at
+        writer.writerow([date, agent, text])
+        f_name.close()

### 2014-07-27 text_cleaner.py

@@ -39,11 +39,22 @@ def extractData(csv_f, month_date):
     for i, row in enumerate(reader_l):
         text = row[2]
         node = row[1]
-        dateb = row[0].split(" ")
-        if month_date:
-            period = dateb[2] + " " + dateb[5]
+        if "-" not in row[0]:
+            dateb = row[0].split(" ")
+            if month_date:
+                period = dateb[2] + " " + dateb[5]
+                period = str(datetime.strptime(period, "%b %Y"))
+            else:
+                period = dateb[1] + " " + dateb[2] + " " + dateb[5]
+                period = str(datetime.strptime(period, "%b %d %Y"))
         else:
-            period = dateb[1] + " " + dateb[2] + " " + dateb[5]
+            dateb = row[0].split(" ")[0].split("-")
+            if month_date:
+                period = dateb[1] + " " + dateb[0]
+                period = str(datetime.strptime(period, "%m %Y"))
+            else:
+                period = dateb[1] + " " + dateb[2] + " " + dateb[0]
+                period = str(datetime.strptime(period, "%m %d %Y"))
         text = text.lower()
         text = rx.sub(" ", text).strip()
         for w in word_tokenize(text):

### 2014-07-28 review_data.py
monthly data

@@ -1,0 +1,50 @@
+from datetime import datetime
+import matplotlib.pyplot as plt
+import csv
+import pandas as pd
+import random
+
+
+def buildSubsetData(csv_f, var_names, date_var, rand_n):
+    """takes a random subset of the data to test the code"""
+
+    reader = csv.reader(open(csv_f, "rb"))
+    data = [r for r in reader]
+    random_mx = len(data)
+    data = [data[random.randint(0, random_mx)] for i in range(rand_n)]
+    data = pd.DataFrame(data, columns=var_names)
+    data[date_var] = data[date_var].apply(pd.to_datetime)
+    data["month"] = data[date_var].apply(lambda x: x.month)
+    data["day"] = data[date_var].apply(lambda x: x.day)
+    data["year"] = data[date_var].apply(lambda x: x.year)
+    data["monthyear"] = data[date_var].apply(lambda x: datetime(x.year, x.month, 1))
+    data["count"] = data["count"].astype(int)
+    return data
+
+
+def buildData(csv_f, var_names, date_var):
+    """builds the dataset"""
+
+    reader = csv.reader(open(csv_f, "rb"))
+    data = [r for r in reader]
+    data = pd.DataFrame(data, columns=var_names)
+    data[date_var] = data[date_var].apply(pd.to_datetime)
+    data["month"] = data[date_var].apply(lambda x: x.month)
+    data["day"] = data[date_var].apply(lambda x: x.day)
+    data["year"] = data[date_var].apply(lambda x: x.year)
+    data["monthyear"] = data[date_var].apply(lambda x: datetime(x.year, x.month, 1))
+    data["count"] = data["count"].astype(int)
+    return data
+
+
+def monthlyWordCount(data):
+    """generates the word count for each month"""
+
+    return data.groupby("monthyear")["count"].sum()
+
+
+def plotMonthlyWordC(word_count):
+    """plots the monthly word count"""
+
+    word_count.plot(xlabel)
+    plt.savefig(fig_name)

### 2014-07-28 run_data_review.py

@@ -1,0 +1,14 @@
+from review_data import *
+import sys
+import cPickle
+
+
+# data = buildSubsetData(sys.argv[1], ["word", "date", "count"], "date", 5000)
+# print "got test data"
+
+data = buildData(sys.argv[1], ["word", "date", "node", "count"], "date")
+print "got real data"
+
+# monthly word count
+word_count = monthlyWordCount(data)
+plotMonthlyWordC(sys.argv[2])

### 2014-07-28 review_data.py
word count

@@ -43,8 +43,20 @@ def monthlyWordCount(data):
     return data.groupby("monthyear")["count"].sum()
 
 
-def plotMonthlyWordC(word_count):
+def wordCount(data):
+    """generates the total count for each word"""
+
+    return data.groupby("word")["count"].sum()
+
+
+def plotMonthlyWordC(m_word_count, fig_name):
     """plots the monthly word count"""
 
-    word_count.plot(xlabel)
+    m_word_count.plot(title="Word Count")
     plt.savefig(fig_name)
+
+
+def plotWordC(word_count, fig_name):
+    """plots the total word count, density"""
+
+    plt.hist(word_count, bins=100, title="Word Count Density")

### 2014-07-28 run_data_review.py

@@ -1,14 +1,21 @@
 from review_data import *
 import sys
 import cPickle
+import os
 
+
+os.chdir(sys.argv[1])
 
 # data = buildSubsetData(sys.argv[1], ["word", "date", "count"], "date", 5000)
 # print "got test data"
 
-data = buildData(sys.argv[1], ["word", "date", "node", "count"], "date")
+data = buildData(sys.argv[2], ["word", "date", "node", "count"], "date")
 print "got real data"
 
 # monthly word count
-word_count = monthlyWordCount(data)
-plotMonthlyWordC(sys.argv[2])
+m_word_count = monthlyWordCount(data)
+plotMonthlyWordC(m_word_count, sys.argv[3])
+
+# total word count
+word_count = wordCount(data)
+plotWordC(word_count, sys.argv[4])

### 2014-07-28 review_data.py
plot top words

@@ -43,16 +43,48 @@ def monthlyWordCount(data):
     return data.groupby("monthyear")["count"].sum()
 
 
+def monthlyUniqueWordC(data):
+    """generates the unique word count monthly"""
+
+    return data.groupby("monthyear")["count"].size()
+
+
 def wordCount(data):
     """generates the total count for each word"""
 
     return data.groupby("word")["count"].sum()
 
 
+def topWords(data, t_limit):
+    """gets the top words"""
+
+    sort_data = data.groupby("word")["count"].sum()
+    sort_data.sort()
+    return sort_data[-t_limit:]
+
+
+def plotMonthlyTopWords(data, t_words, fig_name):
+    """plots the top words"""
+
+    plt.figure()
+    for w in t_words.index:
+        # t = data[data["word"] == w].groupby("monthyear")["count"].sum().plot()
+        data[data["word"] == w].groupby("monthyear")["count"].sum().plot(label=w)
+    plt.legend()
+    plt.savefig(fig_name)
+
+
 def plotMonthlyWordC(m_word_count, fig_name):
     """plots the monthly word count"""
 
     m_word_count.plot(title="Word Count")
+    plt.savefig(fig_name)
+
+
+def plotMonthlyUniqueWordC(um_word_count, fig_name):
+    """plots the unique monthly word count"""
+
+    um_word_count.plot(title="Unique Word Count")
     plt.savefig(fig_name)
 
 

### 2014-07-28 run_data_review.py

@@ -16,6 +16,14 @@ print "got real data"
 m_word_count = monthlyWordCount(data)
 plotMonthlyWordC(m_word_count, sys.argv[3])
 
+# unique monthly word count
+um_word_count = monthlyUniqueWordC(data)
+plotMonthlyUniqueWordC(um_word_count, sys.argv[4])
+
 # total word count
 word_count = wordCount(data)
-plotWordC(word_count, sys.argv[4])
+plotWordC(word_count, sys.argv[5])
+
+# monthly top words
+top_words = topWords(data, int(sys.argv[6]))
+plotMonthlyTopWords(data, top_words, sys.argv[7])

### 2014-07-28 review_data.py
get nodes

@@ -68,7 +68,6 @@ def plotMonthlyTopWords(data, t_words, fig_name):
 
     plt.figure()
     for w in t_words.index:
-        # t = data[data["word"] == w].groupby("monthyear")["count"].sum().plot()
         data[data["word"] == w].groupby("monthyear")["count"].sum().plot(label=w)
     plt.legend()
     plt.savefig(fig_name)
@@ -92,3 +91,35 @@ def plotWordC(word_count, fig_name):
     """plots the total word count, density"""
 
     plt.hist(word_count, bins=100, title="Word Count Density")
+
+
+# The remainder of this code will only work with the network data
+
+def nodeWordCount(data):
+    """gets the word count for each node"""
+
+    return data.groupby("node")["count"].sum()
+
+
+def topNodes(data, n_limit):
+    """get the top nodes"""
+
+    sort_data = data.groupby("node")["count"].sum()
+    sort_data.sort()
+    return sort_data[-n_limit:]
+
+
+def plotMonthlyTopNodes(data, t_nodes, fig_name):
+    """plots the top nodes"""
+
+    plt.figure()
+    for n in t_nodes.index:
+        data[data["node"] == n].groupby("monthyear")["count"].sum().plot(label=n)
+    plt.legend()
+    plt.savefig(fig_name)
+
+
+def plotNodeWordC(n_word_count, fig_name):
+    """plots the word count for each node"""
+
+    plt.hist(n_word_count, bins=100, title="Node Word Count Density")

### 2014-07-28 run_data_review.py

@@ -27,3 +27,11 @@ plotWordC(word_count, sys.argv[5])
 # monthly top words
 top_words = topWords(data, int(sys.argv[6]))
 plotMonthlyTopWords(data, top_words, sys.argv[7])
+
+# node word count
+n_word_count = nodeWordCount(data)
+plotNodeWordC(n_word_count, sys.argv[8])
+
+# monthly top nodes
+top_nodes = topNodes(data, int(sys.argv[9]))
+plotMonthlyTopNodes(data, top_nodes, sys.argv[10])

### 2014-07-28 review_data.py
review data

@@ -101,6 +101,14 @@ def nodeWordCount(data):
     return data.groupby("node")["count"].sum()
 
 
+def docWordCount(data):
+    """gets the mean word count for each period"""
+
+    subset = data
+    subset["sum"] = subset.groupby(["node", "monthyear"])["count"].transform(sum)
+    return subset.groupby("monthyear").mean()
+
+
 def topNodes(data, n_limit):
     """get the top nodes"""
 
@@ -119,7 +127,15 @@ def plotMonthlyTopNodes(data, t_nodes, fig_name):
     plt.savefig(fig_name)
 
 
+def plotDocWordC(d_word_count, fig_name):
+    """plots the document word count"""
+
+    d_word_count.plot(title="Node Month Average Word Count")
+    plt.savefig(fig_name)
+
+
 def plotNodeWordC(n_word_count, fig_name):
     """plots the word count for each node"""
 
     plt.hist(n_word_count, bins=100, title="Node Word Count Density")
+    plt.savefig(fig_name)

### 2014-07-28 run_data_review.py

@@ -35,3 +35,7 @@ plotNodeWordC(n_word_count, sys.argv[8])
 # monthly top nodes
 top_nodes = topNodes(data, int(sys.argv[9]))
 plotMonthlyTopNodes(data, top_nodes, sys.argv[10])
+
+# monthly average doc word count
+d_word_count = docWordCount(data)
+plotDocWordC(d_word_count, sys.argv[11])

### 2014-08-20 LDA_model.R
local changes

@@ -3,7 +3,7 @@ library(topicmodels)
 library(ggplot2)
 library(MASS)
 
-tab <- read.csv("8-11-2014_node_data.csv", header=FALSE)
+tab <- read.csv("8-12-2014_node_data.csv", header=FALSE)
 
 # fix datetime
 tab[,2] <- as.POSIXct(tab[,2])
@@ -34,8 +34,14 @@ save.image("DTM.RData")
 
 model = LDA(dtm, 20)
 
+# save the model image
+save.image("20_Topic_LDA.RData")
+
 # correlation code
 K <- 20
+xi2 <- 20
+delta2 <- 20
+eta <- 0
 
 # ols code
 
@@ -48,7 +54,7 @@ reg_l <- list()
 p_l <- list()
 
 # iterate through the nodes
-for(i in 1:20){
+for(i in 1:K){
     reg_mat <- matrix(NA, ln_nodes, ln_nodes)
     p_mat <- matrix(NA, ln_nodes, ln_nodes)
     for(j in 1:ln_nodes){
@@ -57,7 +63,7 @@ for(i in 1:20){
         for(k in 1:ln_nodes){
             reg_data[paste("I", k, sep="")] <- model@gamma[,i][((k-1)*stp + 1):(k*stp -1)]
         }
-        mod <- lm(D ~ ., data=reg_data)
+        mod <- glm(D ~ ., data=reg_data, family=binomial(logit))
         for(k in 1:ln_nodes){
             reg_mat[j, k] <- coef(summary(mod))[,1][k]
             p_mat[j, k] <- coef(summary(mod))[,4][k]
@@ -89,10 +95,7 @@ for(i in 1:ln_nodes){
 }
 
 
-I_K <- diag(20)
 I_N <- diag(ln_nodes)
-
-eta <- 1.5
 
 # mcmc results
 gamma <- matrix(NA, ln_nodes, ln_nodes)

### 2014-08-20 clean_data.py

@@ -147,13 +147,10 @@ def cleanRData(i_csv_f, o_csv_f):
     writer = csv.writer(open(o_csv_f, "wb"))
     mx_date = 0
     for n in node_dict:
-<<<<<<< HEAD
-=======
         for d in node_dict[n].keys():
             if len(node_dict[n][d]) < 10:
                 del node_dict[n][d]
     for n in node_dict:
->>>>>>> 21fd306333f7e18e9d29d47286c0baaf33fe02a3
         t_date = len(node_dict[n])
         if t_date > mx_date:
             mx_date = t_date

### 2014-08-20 LDA_model.R
local changes

@@ -3,7 +3,7 @@ library(topicmodels)
 library(ggplot2)
 library(MASS)
 
-tab <- read.csv("8-11-2014_node_data.csv", header=FALSE)
+tab <- read.csv("8-19-2014_node_data.csv", header=FALSE)
 
 # fix datetime
 tab[,2] <- as.POSIXct(tab[,2])
@@ -35,7 +35,7 @@ save.image("DTM.RData")
 model = LDA(dtm, 20)
 
 # correlation code
-K <- 20
+K <- 50
 
 # ols code
 
@@ -48,7 +48,7 @@ reg_l <- list()
 p_l <- list()
 
 # iterate through the nodes
-for(i in 1:20){
+for(i in 1:K){
     reg_mat <- matrix(NA, ln_nodes, ln_nodes)
     p_mat <- matrix(NA, ln_nodes, ln_nodes)
     for(j in 1:ln_nodes){

### 2014-08-21 LDA_model.R
truth code

@@ -49,6 +49,60 @@ nodes <- unique(tab[,1])
 ln_nodes <- length(nodes)
 stp <- length(tab[,1]) / ln_nodes
 
+# convert topics into mat
+top_mat <- matrix(NA, ln_nodes, stp)
+topics <- topics(model)
+for(i in 1:ln_nodes){
+    for(j in 1:stp){
+        top_mat[i, j] <- topics[(i - 1) * ln_nodes + j]
+    }
+}
+
+# conditional prob
+cond_prob_mat <- matrix(NA, ln_nodes, ln_nodes)
+# most likely topic in each date node pair
+
+
+# iterate through nodes
+for(i in 1:ln_nodes){
+    for(j in 1:ln_nodes){
+        i_d <- top_mat[i, 2:stp]
+        j_d <- top_mat[j, 1:(stp-1)]
+        ln_data <- length(i_d)
+        cond_prob_mat[i, j] <- sum(i_d == j_d) / ln_data
+    }
+}
+
+
+# generate truth value
+truth_ind <- matrix(NA, K, stp - 1)
+
+for(i in 1:K){
+    for(j in 2:stp){
+        truth_ij <- 0
+        prev_ind <- which(top_mat[,j-1] == i)
+        curr_ind <- which(top_mat[,j] == i)
+        for(k in curr_ind){
+            belief <- 1
+            for(q in prev_ind){
+                belief <- belief * (1 - cond_prob_mat[k, q])
+            }
+            truth_ij <- truth_ij + belief
+        }
+        truth_ij <- truth_ij / ln_nodes
+        truth_ind[i, j - 1] <- truth_ij
+    }
+} 
+            
+# generate depedent truth
+truth_dep <- matrix(NA, K, stp - 1)
+for(i in 1:K){
+    for(j in 2:stp){
+        truth_dep[i, j - 1] <- sum(top_mat[,j] == i) / ln_nodes
+    }
+}
+
+
 # initalize storage
 reg_l <- list()
 p_l <- list()

### 2014-08-22 LDA_model.R
full results

@@ -3,7 +3,7 @@ library(topicmodels)
 library(ggplot2)
 library(MASS)
 
-tab <- read.csv("8-19-2014_node_data.csv", header=FALSE)
+tab <- read.csv("8-21-2014_node_data.csv", header=FALSE)
 
 # fix datetime
 tab[,2] <- as.POSIXct(tab[,2])
@@ -38,7 +38,7 @@ model = LDA(dtm, 20)
 save.image("20_Topic_LDA.RData")
 
 # correlation code
-K <- 50
+K <- 20
 xi2 <- 20
 delta2 <- 20
 eta <- 0
@@ -100,6 +100,46 @@ for(i in 1:K){
     for(j in 2:stp){
         truth_dep[i, j - 1] <- sum(top_mat[,j] == i) / ln_nodes
     }
+}
+
+
+# generate the risk for a node for each period
+topic_risk <- list()
+for(i in 1:K){
+    t_mat <- matrix(NA, ln_nodes, stp - 1)
+    for(j in 2:stp){
+        prev_ind <- which(top_mat[,j - 1] == i)
+        for(k in 1:ln_nodes){
+            node_risk <- sum(cond_prob_mat[k, prev_ind])
+            t_mat[k, j - 1] <- node_risk
+        }
+    }
+    topic_risk[[i]] <- t_mat
+}
+
+
+# prduces expected value in each pair
+expected_val_mat <- matrix(NA, ln_nodes, stp - 1)
+
+for(i in 1:ln_nodes){
+    for(j in 2:stp){
+        mx <- 0
+        mx_ind <- 1
+        for(k in 1:K){
+            if(topic_risk[[k]][i, j - 1] > mx){
+                mx <- topic_risk[[k]][i, j - 1]
+                mx_ind <- k
+            }
+        }
+        expected_val_mat[i, j - 1] <- mx_ind
+    }
+}
+
+            
+# quality of firm
+influence <- rep(NA, ln_nodes)
+for(i in 1:ln_nodes){
+    influence[i] <- sum(cond_prob_mat[,i])
 }
 
 

### 2014-08-22 LDA_model.R
clean code

@@ -1,8 +1,10 @@
+#### load libraries
 library(tm)
 library(topicmodels)
 library(ggplot2)
 library(MASS)
 
+#### load data
 tab <- read.csv("8-21-2014_node_data.csv", header=FALSE)
 
 # fix datetime
@@ -32,19 +34,19 @@ dtm <- DocumentTermMatrix(corpus)
 # save the document term matrix data
 save.image("DTM.RData")
 
+#### LDA model
 model = LDA(dtm, 20)
 
 # save the model image
 save.image("20_Topic_LDA.RData")
 
-# correlation code
+# input values
 K <- 20
 xi2 <- 20
 delta2 <- 20
 eta <- 0
 
-# ols code
-
+# make nodes, the length of nodes and the number of periods
 nodes <- unique(tab[,1])
 ln_nodes <- length(nodes)
 stp <- length(tab[,1]) / ln_nodes
@@ -58,10 +60,8 @@ for(i in 1:ln_nodes){
     }
 }
 
-# conditional prob
+#### Conditional Prob
 cond_prob_mat <- matrix(NA, ln_nodes, ln_nodes)
-# most likely topic in each date node pair
-
 
 # iterate through nodes
 for(i in 1:ln_nodes){
@@ -73,8 +73,8 @@ for(i in 1:ln_nodes){
     }
 }
 
-
-# generate truth value
+#### Generate Truth Value
+# independent truth value
 truth_ind <- matrix(NA, K, stp - 1)
 
 for(i in 1:K){
@@ -94,7 +94,7 @@ for(i in 1:K){
     }
 } 
             
-# generate depedent truth
+# dependent truth value
 truth_dep <- matrix(NA, K, stp - 1)
 for(i in 1:K){
     for(j in 2:stp){
@@ -103,7 +103,7 @@ for(i in 1:K){
 }
 
 
-# generate the risk for a node for each period
+#### Risk for each Node Period
 topic_risk <- list()
 for(i in 1:K){
     t_mat <- matrix(NA, ln_nodes, stp - 1)
@@ -117,8 +117,7 @@ for(i in 1:K){
     topic_risk[[i]] <- t_mat
 }
 
-
-# prduces expected value in each pair
+#### Expected Value for each Node Period
 expected_val_mat <- matrix(NA, ln_nodes, stp - 1)
 
 for(i in 1:ln_nodes){
[…]

### 2014-08-22 paper/paper.tex
small updates
intro methodology

@@
 
-\[p(p_i | T, s_i) = p(p_i | T, \!\{s_j \forall j \in J_{-i}\}) = \prod_{j=1}^{J_{-i}} (1 - \gamma_{ij}) p(p_i | T)\]
+\[p(p_i | T, s_i) = p(p_i | T, \{!s_j \forall j \in J_{-i}\}) = \prod_{j=1}^{J_{-i}} (1 - \gamma_{ij}) p(p_i | T)\]
 
@@
 Firms that are more risk averse should have a higher $\beta_2$ relative to the rest of the population of firms. NOTE: This may also fit better in a different section.
+
+\section{Methodology}
+
+The data was scraped from a list of Twitter handles for US newspapers from the US Newspaper List (USNL, http://www.usnpl.com/).
+From this list __ accounts were used that had a high enough frequency of tweets.
+We experimented with several different periods.
+A period consists of the text of all tweets made by a newspaper in a given time frame, 3 hours, 6 hours, 12 hours, 24 hours, 7 days.
+For each period the text was cleaned in the following way.
+All upper case characterds were replaced with lower case characters, all punctuation was removed, all numbers were removed, all white space was removed, urls were removed, this is particularlly important for Twitter since many tweets include urls (HOW MANY?).
+Finally, stop words are removed, this is done using the English stop words list from the tm library (for text mining) in R.
+All the analysis was done in R and the code is available in an appendix.
+Once the data was cleaned it is turned into a document term matrix to make it usable for LDA.
+
+The estimate the influence that each newspaper has on the other newspapers we start with the topic proportions produced from the LDA models.
+These are the $\theta$ values that represent the parameters for a multinomial model from which the words are selected.
+They essentially give a measure of how prevelant a given topic is in a given document.
+In this case each document represents a newspaper period pair.
+Using these topic proportions you can produce an estimate of the most likely topic for each document.
+Using these most likely topics we build a matrix of conditional probabilities, representing that a given topic observed in the ith newspaper in period t will appear in the jth newspaper in period t+1.
+
+\[P(T_{jt+1} | T_{it})\]
+
+This matrix can be used to represent the influence that each newspapers has on the other newspapers in the graph.
 

### 2014-08-22 paper/paper.tex
add truth

@@
 
+Using the graph of newspapers and periods we are able to build a measure of the likelihood of each topic for each period.
+Naively this could be done by treating each newspaper as an observation and determing the proportion of each topic in each period.
+Unfortunately, this ignores one possible concern which is that each newspaper is unlikely to be indpendent.
+As a result we use an alternative measure as well.
+Our measure is the probability that the observations we are making are independent of influence of other newspapers.
+We calculate this measure by getting the probability that each observation is independent,
+
+\[P(TI_{it+1}) = \prod_{j=1}^J (1 - P(T_{it+1} | T_{jt}))P(T_{it+1})\]
+
+where J is the number of newspapers that reported on a topic in the previous period.  We use both this measure and the naive measure later in the paper.
+
 \section{Implementation}

### 2014-08-22 paper/paper.tex
Update paper.tex

@@
 
+Next we estimate the expected value for each node period.
+This is estimated by taking the influence for each newspaper and calculated the weighted sum of newspapers that are producing a given topic in period t.
+This weighted sum produces a value for each topic.
+The maximum of these values in then chosen for each newspaper and period producing the expected value with the corresponding topic.
+
+Finally, we estimate the total influence of each newspaper by summing the individual influences on each other newspaper.
+
 \section{Implementation}

### 2014-09-26 LDA_model.R
local changes

@@ -41,7 +41,7 @@ model = LDA(dtm, 20)
 save.image("20_Topic_LDA.RData")
 
 # input values
-K <- 20
+K <- 50
 xi2 <- 20
 delta2 <- 20
 eta <- 0

### 2014-09-26 paper/paper.tex

@@
 
-We investigate the impact that bias and trust has on how information is diffused within a network of agents.
-We use this model to investigate the information diffusion characteristics of 2 different data sets.
+We investigate the impact that bias and trust has on how information is diffused within a network of news firms.
+We use this model to investigate the information diffusion characteristics of a novel data set of tweets form US news firms.
 We also use our measures of trust to estimate some probability for the real state of the world.
@@
 
-We examine two novel data sets to investigate this model, the first is a data set of tweets for a list of roughly 3000 media firms in the United States from June to August of 2014.
-Additionally, we consider a data set of articles taken from the preprint repository ArXiv.
-We build a trust network for both of these data sets based on a number of different measures of bias and use this to investigate our model.
-To investigate this model we use a graphical variant of the dynamic topic model to estimate trust between agents.
+We examine two novel data sets to investigate this model, the first is a data set of tweets for a list of roughly 2000 media firms in the United States from June to August of 2014.
+We build an trust network for the data set based on a number of different measures of bias and use this to investigate our model.
+To investigate this model we use a graphical topic model to estimate trust between agents.
 
@@
 2011.}.
-
-The literature on slant in academia is more limited than in the media case, perhaps because the impact is less apparent.
-Much of the literature focuses on divisions of citation networks, though some look at text clustering including one example presented below.
-Onder and Tervio look at the division of citation networks into "freshwater" and "saltwater" departments for economics.
-They find that the division is very real and significant in a number of cases\footnote{Onder and Tervio.
-Is Economics a House Divided?
-Analysis of Citation Networks.
-2014.}.
 
